% -*- coding: utf-8 -*-

% \chapter{References}
% \markboth{REFERENCES}{REFERENCES}
% \begin{description}
% \setlength{\itemsep}{0pt}
% %\setlength{\parsep}{0pt}
% %\setlength{\parindent}{0pt}
% %\setlength{\parskip}{0pt}
% \footnotesize

\begin{thebibliography}{999}
\bibitem{Alley:2000}
Alley R.B.  2000. Ice-core evidence of abrupt climate change.
\textit{Proceedings of National Academy of Sciences} 97 (4):
1331--1334.
%
% \item [Alley]R.B. 2000. Ice-core evidence of abrupt climate change.
%   \textit{Proceedings of National Academy of Sciences} 97 (4):
%   1331--1334.

\bibitem{Apel:1987}
Apel J.R.  1987. \textit{Principles of Ocean Physics}.  New York:
Academic Press.
%
% \item[Apel]J.R. 1987. \textit{Principles of Ocean Physics}.  New York:
%   Academic Press.

\bibitem{Anderson:2005}
Anderson J.D.  2005. Ludwig Prandtl's Boundary Layer.  \textit{Physics
  Today} 58 (12): 42--48.
%
% \item [Anderson]J.D. 2005. Ludwig Prandtl's Boundary
%   Layer. \textit{Physics Today} 58 (12): 42--48.

\bibitem{Andersen:1995}
Andersen O.B., P.L. Woodworth, and R.A. Flather. 1995. Intercomparison
of recent ocean tide models. \textit{J. Geophysical Research} 100
(C12): 25,262--25,282.
%
% \item [Andersen]O.B., P.L. Woodworth, and
%   R.A. Flather. 1995. Intercomparison of recent ocean tide
%   models. \textit{J. Geophysical Research} 100 (C12): 25,262--25,282.

\bibitem{Arthur:1960}
Arthur R.S.  1960. A review of the calculation of ocean currents at
the equator. \textit{Deep-Sea Research} 6 (4): 287--297.
%
% \item [Arthur]R.S. 1960. A review of the calculation of ocean currents
%   at the equator. \textit{Deep-Sea Research} 6 (4): 287--297.

\bibitem{Atlas:1993}
Atlas R., R.N. Hoffman, and S.C. Bloom.  1993. Surface wind velocity
over the oceans. In: \textit{Atlas of satellite observations related
  to global change}. Edited by R. J. Gurney, J. L. Foster and
C. L. Parkinson. 129--140. Cambridge: University Press.
%
% \item [Atlas]R., R.N. Hoffman, and S.C. Bloom. 1993. Surface wind
%   velocity over the oceans. In: \textit{Atlas of satellite
%     observations related to global change}. Edited by R. J. Gurney,
%   J. L. Foster and C. L. Parkinson. 129--140. Cambridge: University
%   Press.

\bibitem{Baker:1981}
Baker D.J.  1981. Ocean instruments and experiment design. In
\textit{Evolution of Physical Oceanography: Scientific Surveys in
  Honor of Henry Stommel}. Edited by B. A. Warren and
C. Wunsch. 396--433. Cambridge: Massachusetts Institute of Technology
Press.
%
% \item [Baker]D.J. 1981. Ocean instruments and experiment design. In
%   \textit{Evolution of Physical Oceanography: Scientific Surveys in
%     Honor of Henry Stommel}. Edited by B. A. Warren and
%   C. Wunsch. 396--433. Cambridge: Massachusetts Institute of
%   Technology Press.

\bibitem{Barnett:1993}
Barnett T.P., M. Latif, N.E. Graham, M. Flugel, S. Pazan, and
W. White.  1993. \textsc{enso} and \textsc{enso}-related
predictability. Part I: Prediction of equatorial Pacific sea surface
temperature in a hybrid coupled ocean-atmosphere
model. \textit{Journal of Climate} 6: 1545--1566.
%
% \item [Barnett]T.P., M. Latif, N.E. Graham, M. Flugel, S. Pazan, and
%   W. White.  1993. \textsc{enso} and \textsc{enso}-related
%   predictability. Part I: Prediction of equatorial Pacific sea surface
%   temperature in a hybrid coupled ocean-atmosphere
%   model. \textit{Journal of Climate} 6: 1545--1566.

\bibitem{Barnier:1995}
Barnier B., L. Siefridt, and P. Marchesiello.  1995. Thermal forcing
for a global ocean circulation model using a three-year climatology of
\textsc{ecmwf} analyses. \textit{Journal of Marine Systems} 6:
393--380.
%
% \item [Barnier]B., L. Siefridt, and P. Marchesiello. 1995. Thermal
%   forcing for a global ocean circulation model using a three-year
%   climatology of \textsc{ecmwf} analyses. \textit{Journal of Marine
%     Systems} 6: 393--380.

\bibitem{Barnston:1999}
Barnston A.G., Y. Hea, and M.H. Glantz.  1999. Predictive Skill of
Statistical and Dynamical Climate Models in SST Forecasts during the
1997--98 El Ni\~{n}o Episode and the 1998 La Ni\~{n}a
Onset. \textit{Bulletin of the American Meteorological Society} 80
(2): 217--243.
%
% \item [Barnston] A.G., Y. Hea, and M.H. Glantz. 1999. Predictive Skill
%   of Statistical and Dynamical Climate Models in SST Forecasts during
%   the 1997--98 El Ni\~{n}o Episode and the 1998 La Ni\~{n}a
%   Onset. \textit{Bulletin of the American Meteorological Society} 80
%   (2): 217--243.

\bibitem{Batchelor:1967}
Batchelor G.K.  1967. \textit{An Introduction to Fluid Dynamics}.
Cambridge: University Press.
%
% \item [Batchelor]G.K. 1967. \textit{An Introduction to Fluid
%   Dynamics}.  Cambridge: University Press.

\bibitem{Baumgartner:1975}
Baumgartner A., and E. Reichel.  1975. \textit{The World Water
  Balance}.  New York: Elsevier.
%
% \item [Baumgartner]A., and E. Reichel. 1975. \textit{The World Water
%   Balance}.  New York: Elsevier.

\bibitem{Beardsley:1997}
Beardsley R.C., A.G. Enriquez, C.A. Friehe, and C.A. Alessi. 1997.
Intercomparison of aircraft and buoy measurements of wind speed and
wind stress during \textsc{smile}. \textit{Journal of Atmospheric and
  Oceanic Technology} 14: 969--977.
%
% \item[Beardsley]R.C., A.G. Enriquez, C.A. Friehe, and
%   C.A. Alessi. 1997.  Intercomparison of aircraft and buoy
%   measurements of wind speed and wind stress during
%   \textsc{smile}. \textit{Journal of Atmospheric and Oceanic
%     Technology} 14: 969--977.

\bibitem{Behringer:1998}
Behringer D.W., M. Ji and A. Leetmaa.  1998. An improved coupled model
for \textsc{enso} prediction and implications for ocean
initialization: Part 1: The ocean data assimilation. \textit{Monthly
  Weather Review} 126(4): 1013--1021.
%
% \item [Behringer]D.W., M. Ji and A. Leetmaa. 1998. An improved coupled
%   model for \textsc{enso} prediction and implications for ocean
%   initialization: Part 1: The ocean data assimilation. \textit{Monthly
%     Weather Review} 126(4): 1013--1021.

\bibitem{Bennett:1992}
Bennett A.F.  1992. \textit{Inverse Methods in Physical Oceanography}.
Cambridge: University Press.
%
% \item [Bennett]A.F.  1992. \textit{Inverse Methods in Physical
%   Oceanography}.  Cambridge: University Press.

\bibitem{Berlinski:1996}
Berlinski D.  1996. The end of materialist science. \textit{Forbes
  ASAP} (December 2, 1996): 146--160.
%
% \item [Berlinski]D. 1996. The end of materialist
%   science. \textit{Forbes ASAP} (December 2, 1996): 146--160.

\bibitem{Binder:1949}
Binder R.C.  1949. \textit{Fluid Mechanics}. Second ed. New York:
Prentice--Hall.
%
% \item [Binder]R.C. 1949. \textit{Fluid Mechanics}. Second ed. New
%   York: Prentice--Hall.

\bibitem{Bjerknes:1966}
Bjerknes J.  1966. The possible response of the atmospheric Hadley
circulation to equatorial anomalies of ocean
temperature. \textit{Tellus} 4: 820-929.
%
% \item [Bjerknes]J. 1966. The possible response of the atmospheric
%   Hadley circulation to equatorial anomalies of ocean
%   temperature. \textit{Tellus} 4: 820-929.

\bibitem{Bjerknes:1972}
Bjerknes J.  1972. Large-scale atmospheric response to the 1964--65
Pacific equatorial warming. \textit{Journal of Physical Oceanography}
2 (3): 212--217.
%
% \item [Bjerknes]J. 1972. Large-scale atmospheric response to the
%   1964--65 Pacific equatorial warming. \textit{Journal of Physical
%     Oceanography} 2 (3): 212--217.

\bibitem{Bjerknes:1910}
Bjerknes V. and J.W. Sandstr\"{o}m. 1910. Dynamic Meteorology and
Hydrography, Part I. Statics. Carnegie Institution of Washington DC,
Publication No. 88.
%
% \item [Bjerknes]V. and J.W. Sandstr\"{o}m. 1910. Dynamic Meteorology
%   and Hydrography, Part I. Statics. Carnegie Institution of Washington
%   DC, Publication No. 88.

\bibitem{Bleck:2002}
Bleck R.  2002. An oceanic general circulation model framed in hybrid
isopycnic-Cartesian coordinates. \textit{Ocean Modeling} 4: 55--88.
%
% \item [Bleck]R. 2002. An oceanic general circulation model framed in
%   hybrid isopycnic-Cartesian coordinates. \textit{Ocean Modeling} 4:
%   55--88.

\bibitem{Blumberg:1987}
Blumberg A.F., and G.L. Mellor.  1987. A description of a
three-dimensional ocean circulation model. In:
\textit{Three-Dimensional Coastal Ocean Models}. Edited by
N. S. Heaps. 1--16. Washington, DC: American Geophysical Union.
%
% \item [Blumberg]A.F., and G.L. Mellor. 1987. A description of a
%   three-dimensional ocean circulation model. In:
%   \textit{Three-Dimensional Coastal Ocean Models}. Edited by
%   N. S. Heaps. 1--16. Washington, DC: American Geophysical Union.

\bibitem{Bond:1992}
Bond G., H. Heinrich, W. Broecker, L. Labeyrie, J. McManus,
J. Andrews, S. Huon, R. Jantschik, S. Clasen, C. Simet, K. Tedesco,
M. Klas, G. Bonani, and S. Ivy. 1992. Evidence for massive discharges
of icebergs into the North Atlantic ocean during the last glacial
period. \textit{Nature} 360, 245--.
%
% \item [Bond]G., H. Heinrich, W. Broecker, L. Labeyrie, J. McManus,
%   J. Andrews, S. Huon, R. Jantschik, S. Clasen, C. Simet, K. Tedesco,
%   M. Klas, G. Bonani, and S. Ivy. 1992. Evidence for massive
%   discharges of icebergs into the North Atlantic ocean during the last
%   glacial period. \textit{Nature} 360, 245--.

\bibitem{Boville:1998}
Boville B.A., and P.R. Gent.  1998. The \textsc{ncar} Climate System
Model, Version One. \textit{Journal of Climate} 11 (6): 1115--1130.
%
% \item [Boville]B.A., and P.R. Gent. 1998. The \textsc{ncar} Climate
%   System Model, Version One. \textit{Journal of Climate} 11 (6):
%   1115--1130.

\bibitem{Bowden:1962}
Bowden K.F.  1962. Turbulence. In: \textit{The Sea Volume 1}. Edited
by M. N.  Hill. 802--825. New York: Interscience Publishers, John
Wiley and Sons.
%
% \item[Bowden]K.F. 1962. Turbulence. In: \textit{The Sea Volume
%   1}. Edited by M. N.  Hill. 802--825. New York: Interscience
%   Publishers, John Wiley and Sons.

\bibitem{Bracewell:1986}
Bracewell R.N.  1986. \textit{The Fourier Transform and Its
  Applications}.  Second, revised ed.  New York: McGraw-Hill
Publishing Company.
%
% \item [Bracewell]R.N. 1986. \textit{The Fourier Transform and Its
%   Applications}.  Second, revised ed.  New York: McGraw-Hill
%   Publishing Company.

\bibitem{Brauer:2008}
Brauer A., G. H. Haug, et al.  2008. An abrupt wind shift in western
Europe at the onset of the Younger Dryas cold period. \textit{Nature
  Geoscience} 1 (8): 520--523.
%
% \item [Brauer]A., G. H. Haug, et al. 2008. An abrupt wind shift in
%   western Europe at the onset of the Younger Dryas cold
%   period. \textit{Nature Geoscience} 1 (8): 520--523.

\bibitem{Broecker:1987}
Broecker W.S.  1987. Unpleasant surprises in the greenhouse?
\textit{Nature} 328: 123--126.
%
% \item [Broecker]W.S. 1987. Unpleasant surprises in the greenhouse?
%   \textit{Nature} 328: 123--126.

\bibitem{Broecker:1997} 
Broecker W.S.  1997. Thermohaline circulation, the Achilles heel of
our climate system: Will man-made \COtwo{} upset the current balance?
\textit{Science} 278 (5343): 1582--1588.
%
% \item [Broecker]W.S. 1997. Thermohaline circulation, the Achilles heel
%   of our climate system: Will man-made CO$_2$ upset the current
%   balance? \textit{Science} 278 (5343): 1582--1588.

\bibitem{Bryan:1969}
Bryan K.  1969. A numerical method for the study of the world ocean.
\textit{Journal of Computational Physics} 4: 347--376.
%
% \item [Bryan] K. 1969. A numerical method for the study of the world
%   ocean.  \textit{Journal of Computational Physics} 4: 347--376.

\bibitem{Bryden:1991}
Bryden H.L. and T.H. Kinder.  1991. Steady two-layer exchange through
the Strait of Gibraltar. \textit{Deep Sea Research} 38 Supplement 1A:
S445--S463.
%
% \item [Bryden]H.L. and T.H. Kinder. 1991. Steady two-layer exchange
%   through the Strait of Gibraltar. \textit{Deep Sea Research} 38
%   Supplement 1A: S445--S463.

\bibitem{Carritt:1959}
Carritt D.E., and J.H. Carpenter.  1959. The composition of sea water
and the salinity-chlorinity-density problems. National Academy of
Sciences-National Research Council, Report 600: 67--86.
%
% \item [Carritt]D.E., and J.H. Carpenter. 1959. The composition of sea
%   water and the salinity-chlorinity-density problems. National Academy
%   of Sciences-National Research Council, Report 600: 67--86.

\bibitem{Cartwright:1999}
Cartwright D.E.  1999. \textit{Tides: A Scientific
  History}. Cambridge, University Press.
%
% \item [Cartwright]D.E. 1999. \textit{Tides: A Scientific
%   History}. Cambridge, University Press.

\bibitem{Cazenave:2001}
Cazenave A., and J.Y. Royer.  2001. Applications to marine
Geophysics. In \textit{Satellite Altimetry and earth
  Sciences}. 407--439. San Diego: Academic Press.
%
% \item [Cazenave]A., and J.Y. Royer. 2001. Applications to marine
%   Geophysics. In \textit{Satellite Altimetry and earth
%     Sciences}. 407--439. San Diego: Academic Press.

\bibitem{Cess:1995}
Cess R.D., M.H. Zhang, P.Minnis, L.Corsetti, E.G. Dutton, B.W. Forgan,
D.P. Garber, W.L. Gates, J.J. Hack, E.F. Harrison, X. Jing,
J.T. Kiehl, C.N.  Long, J.-J. Morcrette, G.L. Potter, V. Ramanathan,
B. Subasilar, C.H. Whitlock, D.F. Young, and Y. Zhou. 1995. Absorption
of solar radiation by clouds: Observations versus
models. \textit{Science} 267 (5197): 496--499.
%
% \item [Cess]R.D., M.H. Zhang, P.Minnis, L.Corsetti, E.G. Dutton,
%   B.W. Forgan, D.P. Garber, W.L. Gates, J.J. Hack, E.F. Harrison,
%   X. Jing, J.T. Kiehl, C.N.  Long, J.-J. Morcrette, G.L. Potter,
%   V. Ramanathan, B. Subasilar, C.H. Whitlock, D.F. Young, and
%   Y. Zhou. 1995. Absorption of solar radiation by clouds: Observations
%   versus models. \textit{Science} 267 (5197): 496--499.

\bibitem{Chambers:1998}
Chambers D.P., B.D. Tapley, and Stewart, R.H.  1998. Measuring heat
storage changes in the equatorial Pacific: A comparison between
\textsc{Topex} altimetry and Tropical Atmo\-sphere-Ocean
buoys. \textit{Journal of Geophysical Research} 103(C9):
18,591--18,597.
%
% \item[Chambers]D.P., B.D. Tapley, and Stewart, R.H. 1998. Measuring
%   heat storage changes in the equatorial Pacific: A comparison between
%   \textsc{Topex} altimetry and Tropical Atmo\-sphere-Ocean
%   buoys. \textit{Journal of Geophysical Research} 103(C9):
%   18,591--18,597.

\bibitem{Charnock:1955}
Charnock H.  1955. Wind stress on a water surface. \textit{Quarterly
  Journal Royal Meteorological Society} 81: 639--640.
%
% \item [Charnock]H. 1955. Wind stress on a water
%   surface. \textit{Quarterly Journal Royal Meteorological Society} 81:
%   639--640.

\bibitem{Chelton:2001}
Chelton D.B., J.C. Ries, B.J. Haines, L.L. Fu, and
P.S. Callahan. 2001. Satellite Altimetry. In: \textit{Satellite
  Altimetry and Earth Sciences: A handbook of techniques and
  applications}. Editors: L.-L. Fu and A. Cazenave. Academic Press:
1--131.
%
% \item [Chelton]D.B., J.C. Ries, B.J. Haines, L.L. Fu, and
%   P.S. Callahan. 2001. Satellite Altimetry. In: \textit{Satellite
%     Altimetry and Earth Sciences: A handbook of techniques and
%     applications}. Editors: L.-L. Fu and A. Cazenave. Academic Press:
%   1--131.

\bibitem{Chen:1995}
Chen D., S.E. Zebiak, A.J. Busalacchi, and M.A. Cane.  1995. An
improved proceedure for El Ni\~{n}o forecasting: Implications for
predictability.  \textit{Science} 269 (5231): 1699--1702.
%
% \item [Chen]D., S.E. Zebiak, A.J. Busalacchi, and M.A. Cane. 1995. An
%   improved proceedure for El Ni\~{n}o forecasting: Implications for
%   predictability.  \textit{Science} 269 (5231): 1699--1702.

\bibitem{Chereskin:1991}
Chereskin T.K., and D. Roemmich.  1991. A comparison of measured and
wind-derived Ekman transport at~$\degrees{11}$~N in the Atlantic
Ocean.  \textit{Journal of Physical Oceanography} 21 (6): 869--878.
%
% \item [Chereskin]T.K., and D. Roemmich. 1991. A comparison of measured
%   and wind-derived Ekman transport at 11\degrees N in the Atlantic
%   Ocean.  \textit{Journal of Physical Oceanography} 21 (6): 869--878.

\bibitem{Chou:2004}
Chou S.-H., E. Nelkin, et al.  2004. A comparison of latent heat
fluxes over global oceans for four flux products. \textit{Journal of
  Climate} 17 (20): 3973--3989.
%
% \item [Chou]S.-H., E. Nelkin, et al. 2004. A comparison of latent heat
%   fluxes over global oceans for four flux products. \textit{Journal of
%     Climate} 17 (20): 3973--3989.

\bibitem{Church:2007}
Church J. A.  2007. Oceans: A Change in Circulation?  \textit{Science}
317 (5840): 908--909.
%
% \item [Church]J. A. 2007. Oceans: A Change in Circulation?
%   \textit{Science} 317 (5840): 908--909.

\bibitem{Clarke:1970}
Clarke G.L., G.C. Ewing, and C.J. Lorenzen.  1970. Spectra of
backscattered light from the sea obtained from aircraft as a measure
of chlorophyll concentration. \textit{Science} 167: 1119--1121.
%
% \item [Clarke]G.L., G.C. Ewing, and C.J. Lorenzen. 1970. Spectra of
%   backscattered light from the sea obtained from aircraft as a measure
%   of chlorophyll concentration. \textit{Science} 167: 1119--1121.

\bibitem{Coakley:1982}
Coakley J.A., and F.P. Bretherton.  1982. Cloud cover from high
resolution scanner data: Detecting and allowing for partially filled
fields of view. \textit{Journal of Geophysical. Research} 87 (C7):
4917--4932.
%
% \item [Coakley]J.A., and F.P. Bretherton. 1982. Cloud cover from high
%   resolution scanner data: Detecting and allowing for partially filled
%   fields of view. \textit{Journal of Geophysical. Research} 87 (C7):
%   4917--4932.

\bibitem{Cooley:1970}
Cooley J.W., P.A. Lewis, and P.D. Welch.  1970. The fast Fourier
transform algorithm: Programming considerations in the calculation of
sine, cosine and Laplace transforms. \textit{Journal of Sound and
  Vibration} 12: 315--337.
%
% \item [Cooley]J.W., P.A. Lewis, and P.D. Welch. 1970. The fast Fourier
%   transform algorithm: Programming considerations in the calculation
%   of sine, cosine and Laplace transforms. \textit{Journal of Sound and
%     Vibration} 12: 315--337.

\bibitem{Couper:1983}
Couper A. Editor.  1983. \textit{The Times Atlas of the Oceans}. New
York: Van Nostrand Reinhold Company.
%
% \item [Couper]A. Editor. 1983. \textit{The Times Atlas of the
%   Oceans}. New York: Van Nostrand Reinhold Company.

\bibitem{Cox:1975}
Cox M.D.  1975. A baroclinic model of the world ocean: Preliminary
results. In: \textit{Numerical Models of Ocean Circulation}:
107--120. Washington, DC: National Academy of Sciences.
%
% \item [Cox]M.D. 1975. A baroclinic model of the world ocean:
%   Preliminary results. In: \textit{Numerical Models of Ocean
%     Circulation}: 107--120. Washington, DC: National Academy of
%   Sciences.

\bibitem{Cromwell:1954}
Cromwell T., R.B. Montgomery, and E.D. Stroup.  1954. Equatorial
undercurrent in Pacific Ocean revealed by new
methods. \textit{Science} 119 (3097): 648--649.
%
% \item [Cromwell]T., R.B. Montgomery, and E.D. Stroup. 1954. Equatorial
%   undercurrent in Pacific Ocean revealed by new
%   methods. \textit{Science} 119 (3097): 648--649.

\bibitem{Cushman-Roisin:1994}
Cushman-Roisin B.  1994. \textit{Introduction to Geophysical Fluid
  Dynamics}.  Englewood Cliffs: Prentice Hall.
%
% \item[Cushman-Roisin]B. 1994. \textit{Introduction to Geophysical
%   Fluid Dynamics}.  Englewood Cliffs: Prentice Hall.

\bibitem{Cutchin:1973}
Cutchin D.L., and R.L. Smith.  1973. Continental shelf waves:
Low-frequency variations in sea level and currents over the Oregon
continental shelf. \textit{Journal of Physical Oceanography} 3 (1):
73--82.
%
% \item[Cutchin]D.L., and R.L. Smith. 1973. Continental shelf waves:
%   Low-frequency variations in sea level and currents over the Oregon
%   continental shelf. \textit{Journal of Physical Oceanography} 3 (1):
%   73--82.

\bibitem{Daley:1991}
Daley R.  1991. \textit{Atmospheric Data Analysis}.  Cambridge:
University Press.
%
% \item [Daley]R. 1991. \textit{Atmospheric Data Analysis}.  Cambridge:
%   University Press.

\bibitem{Danabasoglu:1994}
Danabasoglu G., J.C. McWilliams, and P.R. Gent.  1994. The role of
mesoscale tracer transports in the global ocean
circulation. \textit{Science} 264 (5162): 1123--1126.
%
% \item [Danabasoglu]G., J.C. McWilliams, and P.R. Gent. 1994. The role
%   of mesoscale tracer transports in the global ocean
%   circulation. \textit{Science} 264 (5162): 1123--1126.

\bibitem{Dansgaard:1993}
Dansgaard W., S.J. Johnsen, H.B. Clausen, D. Dahl-Johnsen, N.
Gunderstrup, C.U. Hammer, C. Hvidberg, J. Steffensen,
A. Sveinbj\"{o}rnsobttir, J.  Jouze and G. Bond. 1993. Evidence for
general instability of past climate from a 250-kyr ice core
record. \textit{Nature} 364: 218-220.
%
% \item [Dansgaard]W., S.J. Johnsen, H.B. Clausen, D. Dahl-Johnsen, N.
%   Gunderstrup, C.U. Hammer, C. Hvidberg, J. Steffensen,
%   A. Sveinbj\"{o}rnsobttir, J.  Jouze and G. Bond. 1993. Evidence for
%   general instability of past climate from a 250-kyr ice core
%   record. \textit{Nature} 364: 218-220.

\bibitem{Darnell:1988}
Darnell W.L., F. Staylor, S.K. Gupta, and F,M. Denn. 1988. Estimation
of surface insolation using sun-synchronous satellite
data. \textit{Journal of Climate} 1 (8): 820--835.
%
% \item [Darnell]W.L., F. Staylor, S.K. Gupta, and
%   F,M. Denn. 1988. Estimation of surface insolation using
%   sun-synchronous satellite data. \textit{Journal of Climate} 1 (8):
%   820--835.

\bibitem{Darnell:1992}
Darnell W.L., W.F. Staylor, S.K. Gupta, N.A. Ritchey, and A.C. Wilbur.
1992. Seasonal variation of surface radiation budget derived from
International Satellite Cloud Climatology Project C1
data. \textit{Journal of Geophysical Research} 97: 15,741--15,760.
%
% \item [Darnell]W.L., W.F. Staylor, S.K. Gupta, N.A. Ritchey, and
%   A.C. Wilbur.  1992. Seasonal variation of surface radiation budget
%   derived from International Satellite Cloud Climatology Project C1
%   data. \textit{Journal of Geophysical Research} 97: 15,741--15,760.

\bibitem{Darwin:1911}
Darwin Sir G.H.  1911. \textit{The Tides and Kindred Phenomena in the
  Solar System}. 3rd ed.  London: John Murray.
%
% \item [Darwin]Sir G.H. 1911. \textit{The Tides and Kindred Phenomena
%   in the Solar System}. 3rd ed.  London: John Murray.

\bibitem{DaSilva:1995}
DaSilva A., C.C. Young, and S. Levitus.  1995. Atlas of surface marine
data 1994. Vol. 1: Algorithms and procedures. National Oceanic and
Atmospheric Administration Report.
%
% \item [DaSilva]A., C.C. Young, and S. Levitus. 1995. Atlas of surface
%   marine data 1994. Vol. 1: Algorithms and procedures. National
%   Oceanic and Atmospheric Administration Report.

\bibitem{Davis:1987}
Davis R.A.  1987. \textit{Oceanography: An Introduction to the Marine
  Environment}. Dubuque: Wm. C. Brown Publishers.
%
% \item [Davis]R.A. 1987. \textit{Oceanography: An Introduction to the
%   Marine Environment}. Dubuque: Wm. C. Brown Publishers.

\bibitem{Davis:1981}
Davis R.E., R. DeSzoeke, and P. Niiler.  1981. Variability in the
upper ocean during \textsc{mile}. Part II: Modeling the mixed layer
response. \textit{Deep-Sea Research} 28A (12): 1453--1475.
%
% \item [Davis]R.E., R. DeSzoeke, and P. Niiler. 1981. Variability in
%   the upper ocean during \textsc{mile}. Part II: Modeling the mixed
%   layer response. \textit{Deep-Sea Research} 28A (12): 1453--1475.

\bibitem{Davis:1992}
Davis R.E., D.C. Webb, L.A. Regier, and J. Dufour.  1992. The
Autonomous Lagrangian Circulation Explorer
(\textsc{alace}). \textit{Journal of Atmospheric and Oceanic
  Technology} 9: 264--285.
%
% \item [Davis]R.E., D.C. Webb, L.A. Regier, and J. Dufour. 1992. The
%   Autonomous Lagrangian Circulation Explorer
%   (\textsc{alace}). \textit{Journal of Atmospheric and Oceanic
%     Technology} 9: 264--285.

\bibitem{Defant:1961}
Defant A.  1961. \textit{Physical Oceanography}. New York: Macmillan
Company.
%
% \item [Defant]A. 1961. \textit{Physical Oceanography}. New York:
%   Macmillan Company.

\bibitem{Dietrich:1980}
Dietrich G., K. Kalle, W. Krauss, and
G. Siedler. 1980. \textit{General Oceanography}. 2nd ed. Translated by
Susanne and Hans Ulrich Roll. New York: John Wiley and Sons
(Wiley-Interscience).
%
% \item [Dietrich]G., K. Kalle, W. Krauss, and
%   G. Siedler. 1980. \textit{General Oceanography}. 2nd ed. Translated
%   by Susanne and Hans Ulrich Roll. New York: John Wiley and Sons
%   (Wiley-Interscience).

\bibitem{Dittmar:1884}
Dittmar W.  1884. Report on researches into the composition of ocean
water, collected by the HMS Challenger. \textit{Challenger Reports,
  Physics and Chemistry} 1.
%
% \item [Dittmar]W. 1884. Report on researches into the composition of
%   ocean water, collected by the HMS Challenger. \textit{Challenger
%     Reports, Physics and Chemistry} 1.

\bibitem{Dobson:1914}
Dobson G.M.B.  1914. Pilot balloon ascents at the central flying
school, Upavon, during the year 1913. \textit{Quarterly Journal of the
  Royal Meteorological Society} 40: 123--135.
%
% \item [Dobson]G.M.B. 1914. Pilot balloon ascents at the central flying
%   school, Upavon, during the year 1913. \textit{Quarterly Journal of
%     the Royal Meteorological Society} 40: 123--135.

\bibitem{Domingues:2008}
Domingues C. M., J. A. Church, et al 2008. Improved estimates of
upper-ocean warming and multi-decadal sea-level rise. \textit{Nature}
453 (7198): 1090--1093.
%
% \item [Domingues]C. M., J. A. Church, et al 2008. Improved estimates
%   of upper-ocean warming and multi-decadal sea-level
%   rise. \textit{Nature} 453 (7198): 1090--1093.

\bibitem{Doodson:1922}
Doodson A.T.  1922. Harmonic development of the tide-generating
potential. \textit{Proceedings of the Royal Society of London} A 100:
305--329.
%
% \item [Doodson]A.T. 1922. Harmonic development of the tide-generating
%   potential. \textit{Proceedings of the Royal Society of London} A
%   100: 305--329.

\bibitem{Dorman:1981}
Dorman C.E. and R.H. Bourke.  1981. Precipitation over the Atlantic
ocean, $\degrees{30}$~S to~$\degrees{70}$~N. \textit{Monthly Weather
  Review} 109: 554--563.
%
% \item [Dorman]C.E. and R.H. Bourke. 1981. Precipitation over the
%   Atlantic ocean, 30\degrees S to 70\degrees N. \textit{Monthly
%     Weather Review} 109: 554--563.

\bibitem{Dritschel:1999}
Dritschel D.G., M. de la T. Juarez and M.H.P. Ambaum.  1999. The
three-dimensional vortical nature of atmospheric and oceanic turbulent
flows.  \textit{Physics of Fluids} 11(6): 1512--1520.
%
% \item [Dritschel]D.G., M. de la T. Juarez and M.H.P. Ambaum. 1999. The
%   three-dimensional vortical nature of atmospheric and oceanic
%   turbulent flows.  \textit{Physics of Fluids} 11(6): 1512--1520.

\bibitem{Dushaw:1993}
Dushaw B.D., P.F. Worcester, B.D. Cornuelle, and B.M. Howe. 1993. On
equations for the speed of sound in sea water.  \textit{Journal of the
  Acoustical Society of America} 93: 255--275.
%
% \item [Dushaw]B.D., P.F. Worcester, B.D. Cornuelle, and
%   B.M. Howe. 1993. On equations for the speed of sound in sea water.
%   \textit{Journal of the Acoustical Society of America} 93: 255--275.

\bibitem{Ebbesmeyer:1992}
Ebbesmeyer C.C., and W.J. Ingraham.  1992. Shoe spill in the North
Pacific. \textit{EOS, Transactions of the American Geophysical Union}
73 (34): 361, 365.
%
% \item [Ebbesmeyer]C.C., and W.J. Ingraham. 1992. Shoe spill in the
%   North Pacific. \textit{EOS, Transactions of the American Geophysical
%     Union} 73 (34): 361, 365.

\bibitem{Ebbesmeyer:1994}
Ebbesmeyer C.C., and W.J. Ingraham.  1994. Pacific toy spill fuels
ocean current pathways research. \textit{EOS Transactions of the
  American Geophysical Union} 75 (37): 425, 427, 430.
%
% \item [Ebbesmeyer]C.C., and W.J. Ingraham. 1994. Pacific toy spill
%   fuels ocean current pathways research. \textit{EOS Transactions of
%     the American Geophysical Union} 75 (37): 425, 427, 430.

\bibitem{Eden:1999}
Eden C., and J. Willebrand.  1999. Neutral density revisited.
\textit{Deep-Sea Research} Part II: Topical Studies in
Oceanography. 46: 33--54.
%
% \item [Eden]C., and J. Willebrand. 1999. Neutral density revisited.
%   \textit{Deep-Sea Research} Part II: Topical Studies in
%   Oceanography. 46: 33--54.

\bibitem{Egbert:2000}
Egbert G.B. and R.D. Ray 2000. Significant dissipation of tidal energy
in the deep ocean inferred from satellit altimeter
data. \textit{Nature} 405: 775--778.
%
% \item [Egbert]G.B. and R.D. Ray 2000. Significant dissipation of tidal
%   energy in the deep ocean inferred from satellit altimeter
%   data. \textit{Nature} 405: 775--778.

\bibitem{Ekman:1905}
Ekman V.W.  1905. On the influence of the Earth's rotation on ocean
currents. \textit{Arkiv for Matematik, Astronomi, och Fysik}: 2 (11).
%
% \item [Ekman]V.W. 1905. On the influence of the Earth's rotation on
%   ocean currents. \textit{Arkiv for Matematik, Astronomi, och Fysik}:
%   2 (11).

\bibitem{Emery:1989}
Emery W., and P. Schussel.  1989. Global difference between skin and
bulk sea surface temperatures. \textit{EOS: Transactions of the
  American Geophysical Union} 70 (14): 210--211.
%
% \item [Emery]W., and P. Schussel. 1989. Global difference between skin
%   and bulk sea surface temperatures. \textit{EOS: Transactions of the
%     American Geophysical Union} 70 (14): 210--211.

\bibitem{Feynman:1964}
Feynman R.P., R.B. Leighton, and M. Sands.  1964. \textit{The Feynman
  Lectures on Physics}.  Addison-Wesley Publishing Company.
%
% \item [Feynman]R.P., R.B. Leighton, and M. Sands. 1964. \textit{The
%   Feynman Lectures on Physics}.  Addison-Wesley Publishing Company.

\bibitem{Fofonoff:1983}
Fofonoff N.P., and R.C. Millard.  1983. Algorithms for computation of
fundamental properties of sea water. \textsc{unesco} Technical Papers
in Marine Science 44.
%
% \item [Fofonoff]N.P., and R.C. Millard. 1983. Algorithms for
%   computation of fundamental properties of sea water. \textsc{unesco}
%   Technical Papers in Marine Science 44.

\bibitem{Friedman:1989}
Friedman R.M.  1989. \textit{Appropriating the Weather. Vilhelm
  Bjerknes and the Construction of a Modern Meteorology.}  Ithaca and
London: Cornell University Press.
%
% \item [Friedman]R.M. 1989. \textit{Appropriating the Weather. Vilhelm
%   Bjerknes and the Construction of a Modern Meteorology.}  Ithaca and
%   London: Cornell University Press.

\bibitem{Friedrichs:1993}
Friedrichs M.A.M., and M.M. Hall.  1993. Deep circulation in the
tropical North Atlantic. \textit{Journal of Marine Research} 51 (4):
697--736.
%
% \item [Friedrichs]M.A.M., and M.M. Hall. 1993. Deep circulation in the
%   tropical North Atlantic. \textit{Journal of Marine Research} 51 (4):
%   697--736.

\bibitem{Freilich:1999}
Freilich M.H., and R.S. Dunbar.  1999. The accuracy of the NSCAT 1
vector winds: Comparisons with National Data Buoy Center
buoys. \textit{Journal of Geophysical Research} submitted
%
% \item[Freilich]M.H., and R.S. Dunbar. 1999. The accuracy of the NSCAT
%   1 vector winds: Comparisons with National Data Buoy Center
%   buoys. \textit{Journal of Geophysical Research} submitted

\bibitem{Garabato:2004}
Garabato A.C.N., K.L. Polzin, B.A. King, K.J. Heywood, and
M. Visbeck. 2004. Widespread Intense Turbulent Mixing in the Southern
Ocean. \textit{Science} 303 (5655): 210--213.
%
% \item [Garabato]A.C.N., K.L. Polzin, B.A. King, K.J. Heywood, and
%   M. Visbeck. 2004. Widespread Intense Turbulent Mixing in the
%   Southern Ocean. \textit{Science} 303 (5655): 210--213.

\bibitem{Garabato:2007} 
Garabato A.C.N., D.P. Stevens, A.J. Watson, and
W. Roether. 2007. Short-circuiting of the overturning circulation in
the Antarctic Circumpolar Current. \textit{Nature} 447 (7141):
194--197.
%
% \item [Garabato]A.C.N., D.P. Stevens, A.J. Watson, and
%   W. Roether. 2007. Short-circuiting of the overturning circulation in
%   the Antarctic Circumpolar Current. \textit{Nature} 447 (7141):
%   194--197.

\bibitem{Gargett:1992}
Gargett A.E., and G. Holloway.  1992. Sensitivity of the \textsc{gfdl}
ocean model to different diffusivities of heat and
salt. \textit{Journal of Physical Oceanography} 22 (10): 1158--1177.
%
% \item[Gargett]A.E., and G. Holloway. 1992. Sensitivity of the
%   \textsc{gfdl} ocean model to different diffusivities of heat and
%   salt. \textit{Journal of Physical Oceanography} 22 (10): 1158--1177.

\bibitem{Garrett:2006}
Garrett C.  2006. Turbulent dispersion in the ocean. \textit{Progress
  in Oceanography} 70 (2--4): 113--125.
%
% \item [Garrett]C. 2006. Turbulent dispersion in the
%   ocean. \textit{Progress in Oceanography} 70 (2--4): 113--125.

\bibitem{Gates:1996}
Gates W.L., A. Henderson-Sellers, G.J. Boer, C.K. Folland, A. Kitoh,
B.J. McAvaney, F. Semazzi, N. Smith, A.J. Weaver, and
Q.-C. Zeng. 1996. \textit{Climate Models--Evaluation}. In:
\textit{Climate Change 1995}. Edited by J.T. Houghton, L.G.M. Filho,
B.A. Callander, N. Harris, A. Kattenberg and K.
Maskell. 229--284. Cambridge: University Press.
%
% \item[Gates]W.L., A. Henderson-Sellers, G.J. Boer, C.K. Folland,
%   A. Kitoh, B.J. McAvaney, F. Semazzi, N. Smith, A.J. Weaver, and
%   Q.-C. Zeng. 1996. \textit{Climate Models--Evaluation}. In:
%   \textit{Climate Change 1995}. Edited by J.T. Houghton, L.G.M. Filho,
%   B.A. Callander, N. Harris, A. Kattenberg and K.
%   Maskell. 229--284. Cambridge: University Press.

\bibitem{Gates:1992}
Gates W.L.  1992. \textsc{amip}: The Atmospheric Model Intercomparison
Project.  \textit{Bulletin American Meteorological Society} 73:
1962--1970.
%
% \item [Gates]W.L. 1992. \textsc{amip}: The Atmospheric Model
%   Intercomparison Project.  \textit{Bulletin American Meteorological
%     Society} 73: 1962--1970.

\bibitem{Gent:1990}
Gent P.R., and J.C. McWilliams.  1990. Isopycnal mixing in ocean
circulation models. \textit{Journal of Physical Oceanography} 20:
150--155.
%
% \item[Gent]P.R., and J.C. McWilliams. 1990. Isopycnal mixing in ocean
%   circulation models. \textit{Journal of Physical Oceanography} 20:
%   150--155.

\bibitem{Gleckler:1997}
Gleckler P.J., and B. Weare.  1997. Uncertainties in global ocean
surface heat flux climatologies derived from ship
observance. \textit{Journal of Climate} 10: 2763--2781.
%
% \item [Gleckler]P.J., and B. Weare. 1997. Uncertainties in global
%   ocean surface heat flux climatologies derived from ship
%   observance. \textit{Journal of Climate} 10: 2763--2781.

\bibitem{Gill:1982}
Gill A.E.  1982. \textit{Atmosphere-Ocean Dynamics}. New York:
Academic Press.
%
% \item [Gill]A.E. 1982. \textit{Atmosphere-Ocean Dynamics}. New York:
%   Academic Press.

\bibitem{Gnadadesikan:1999}
Gnadadesikan A.  1999. A simple predictive model for the structure of
the oceanic pycnocline. \textit{Science} 283 (5410): 2077--2079.
%
% \item [Gnadadesikan]A. 1999. A simple predictive model for the
%   structure of the oceanic pycnocline. \textit{Science} 283 (5410):
%   2077--2079.

\bibitem{Goldenberg:1981}
Goldenberg S.B., and J.J. O'Brien. 1981. \textit{Monthly Weather
  Review} 109: 1190.
%
% \item [Goldenberg]S.B., and J.J. O'Brien. 1981. \textit{Monthly
%   Weather Review} 109: 1190.

\bibitem{Goldstein:1965}
Goldstein S.  1965. \textit{Modern Developments in Fluid Dynamics}:
Two Volumes. New York: Dover Publications.
%
% \item [Goldstein]S. 1965. \textit{Modern Developments in Fluid
%   Dynamics}: Two Volumes. New York: Dover Publications.

\bibitem{Gordon:1983}
Gordon H.R., D.K. Clark, J.W. Brown, O.B. Brown, R.H. Evans, and W.W.
Broenkow. 1983. Phytoplankton pigment concentrations in the Middle
Atlantic Bight: comparison of ship determinations and \textsc{czcs}
estimates. \textit{Applied Physics} 22 (1): 20-36.
%
% \item [Gordon]H.R., D.K. Clark, J.W. Brown, O.B. Brown, R.H. Evans,
%   and W.W.  Broenkow. 1983. Phytoplankton pigment concentrations in
%   the Middle Atlantic Bight: comparison of ship determinations and
%   \textsc{czcs} estimates. \textit{Applied Physics} 22 (1): 20-36.

\bibitem{Gouretski:1995}
Gouretski V., and K. Jancke.  1995. A consistent pre-\textsc{woce}
hydrographic data set for the south Atlantic: Station data and gridded
fields.  \textsc{woce} Report No. 127/95.
%
% \item [Gouretski]V., and K. Jancke. 1995. A consistent
%   pre-\textsc{woce} hydrographic data set for the south Atlantic:
%   Station data and gridded fields.  \textsc{woce} Report No. 127/95.

\bibitem{Graber:2006}
Graber H.C., V.J. Cardone, R.E. Jensen, D.N. Slinn, S.C. Hagen,
A.T. Cox, M.D. Powell, and C. Grassl. 2006. Coastal Forecasts and
Storm Surge Predictions for Tropical Cyclones: A Timely Partnership
Program. \textit{Oceanography} 19 (1): 131--141.
%
% \item [Graber]H.C., V.J. Cardone, R.E. Jensen, D.N. Slinn, S.C. Hagen,
%   A.T. Cox, M.D. Powell, and C. Grassl. 2006. Coastal Forecasts and
%   Storm Surge Predictions for Tropical Cyclones: A Timely Partnership
%   Program. \textit{Oceanography} 19 (1): 131--141.

\bibitem{Grassl:2000}
Grassl H.  2000. Status and improvements of coupled general
circulation models. \textit{Science} 288 (5473): 1991--1997.
%
% \item [Grassl]H. 2000. Status and improvements of coupled general
%   circulation models. \textit{Science} 288 (5473): 1991--1997.

\bibitem{Gregg:1987}
Gregg M.C.  1987. Diapycnal mixing in the thermocline: A review.
\textit{Journal of Geophysical Research} 92 (C5): 5,249--5,289.
%
% \item[Gregg]M.C. 1987. Diapycnal mixing in the thermocline: A review.
%   \textit{Journal of Geophysical Research} 92 (C5): 5,249--5,289.

\bibitem{Gregg:1991}
Gregg M.C.  1991. The study of mixing in the ocean: a brief history.
\textit{Oceanography} 4 (1): 39--45.
%
% \item [Gregg]M.C. 1991. The study of mixing in the ocean: a brief
%   history.  \textit{Oceanography} 4 (1): 39--45.

\bibitem{Hackett:1995} 
Hackett B., L.P. Roed, B. Gjevik, E.A. Martinsen, and
L.I. Eide. 1995. A review of the Metocean Modeling Project
(\textsc{mompop}) Part 2: Model validation study. In:
\textit{Quantitative Skill Assessment for Coastal Ocean
  Models}. Edited by D. R. Lynch and
A. M. Davies. 307--327. Washington DC: American Geophysical Union.
%
% \item [Hackett]B., L.P. Roed, B. Gjevik, E.A. Martinsen, and
%   L.I. Eide. 1995. A review of the Metocean Modeling Project
%   (\textsc{mompop}) Part 2: Model validation study. In:
%   \textit{Quantitative Skill Assessment for Coastal Ocean
%     Models}. Edited by D. R. Lynch and
%   A. M. Davies. 307--327. Washington DC: American Geophysical Union.

\bibitem{Haidvogel:1998}
Haidvogel D.B., and A. Beckmann.  1998. Numerical models of the
coastal ocean. In: \textit{The Sea, Volume 10}. Edited by K. H. Brink
and A. R. Robinson. 457--482. New York: John Wiley and Sons.
%
% \item [Haidvogel]D.B., and A. Beckmann. 1998. Numerical models of the
%   coastal ocean. In: \textit{The Sea, Volume 10}. Edited by
%   K. H. Brink and A. R. Robinson. 457--482. New York: John Wiley and
%   Sons.

\bibitem{Haidvogel:1999}
Haidvogel D.B. and A. Beckmann.  1999. \textit{Numerical Ocean
  Circulation Modeling}. London, Imperial College Press.
%
% \item [Haidvogel]D.B. and A. Beckmann. 1999. \textit{Numerical Ocean
%   Circulation Modeling}. London, Imperial College Press.

\bibitem{Hall:1982}
Hall M.M., and H.L. Bryden.  1982. Direct estimates and mechanisms of
ocean heat transport. \textit{Deep-Sea Research} 29: 339--359.
%
% \item [Hall]M.M., and H.L. Bryden. 1982. Direct estimates and
%   mechanisms of ocean heat transport. \textit{Deep-Sea Research} 29:
%   339--359.

\bibitem{Harrison:1989}
Harrison D.E.  1989. On climatological monthly mean wind stress and
wind stress curl fields over the world ocean. \textit{Journal of
  Climate} 2: 57.
%
% \item [Harrison]D.E. 1989. On climatological monthly mean wind stress
%   and wind stress curl fields over the world ocean. \textit{Journal of
%     Climate} 2: 57.

\bibitem{Harrison:1996}
Harrison D.E., and N.K. Larkin.  1996. The \textsc{coads} sea level
pressure signal: A near-global el Ni\~{n}o composite and time series
view, 1946--1993.  \textit{Journal of Climate} 9 (12): 3025--3055.
%
% \item [Harrison]D.E., and N.K. Larkin. 1996. The \textsc{coads} sea
%   level pressure signal: A near-global el Ni\~{n}o composite and time
%   series view, 1946--1993.  \textit{Journal of Climate} 9 (12):
%   3025--3055.

\bibitem{Harrison:1998}
Harrison D.E. and N.K. Larkin 1998. El Ni\~{n}o-Southern Oscillation
sea surface temperature and wind anomalies,
1946--1993. \textit{Reviews of Geophysics} 36 (3): 353--399.
%
% \item [Harrison]D.E. and N.K. Larkin 1998. El Ni\~{n}o-Southern
%   Oscillation sea surface temperature and wind anomalies,
%   1946--1993. \textit{Reviews of Geophysics} 36 (3): 353--399.

\bibitem{Hartmann:1994}
Hartmann D.L.  1994. \textit{Global Physical Climatology}.  Academic
Press.
%
% \item [Hartmann]D.L. 1994. \textit{Global Physical Climatology}.
%   Academic Press.

\bibitem{Hasselmann:1961}
Hasselmann K.  1961. On the non-linear energy transfer in a
gravity-wave spectrum Part 1. General theory. \textit{Journal of Fluid
  Mechanics} 12 (4): 481--500.
%
% \item[Hasselmann]K. 1961. On the non-linear energy transfer in a
%   gravity-wave spectrum Part 1. General theory. \textit{Journal of
%     Fluid Mechanics} 12 (4): 481--500.

\bibitem{Hasselmann:1963a}
Hasselmann K.  1963. On the non-linear energy transfer in a gravity
wave spectrum. Part 2. Conservation theorems; wave-particle analogy;
irreversibility.  \textit{Journal of Fluid Mechanics} 15 (2):
273--281.
%
% \item[Hasselmann]K. 1963a. On the non-linear energy transfer in a
%   gravity wave spectrum. Part 2. Conservation theorems; wave-particle
%   analogy; irreversibility.  \textit{Journal of Fluid Mechanics} 15
%   (2): 273--281.

\bibitem{Hasselmann:1963b}
Hasselmann K.  1963. On the non-linear energy transfer in a gravity
wave spectrum. Part 3. Evaluation of the energy flux and swell-sea
interaction for a Neumann spectrum. \textit{Journal of Fluid
  Mechanics}. 15 (3): 385--398.
%
% \item[Hasselmann]K. 1963b. On the non-linear energy transfer in a
%   gravity wave spectrum. Part 3. Evaluation of the energy flux and
%   swell-sea interaction for a Neumann spectrum. \textit{Journal of
%     Fluid Mechanics}. 15 (3): 385--398.

\bibitem{Hasselmann:1966}
Hasselmann K.  1966. Feynman diagrams and interaction rules of
wave-wave scattering processes. \textit{Reviews of Geophysical}. 4
(1): 1--32.
%
% \item[Hasselmann]K. 1966. Feynman diagrams and interaction rules of
%   wave-wave scattering processes. \textit{Reviews of Geophysical}. 4
%   (1): 1--32.

\bibitem{Hasselmann:1970}
Hasselmann K.  1970. Wind--driven inertial
oscillations. \textit{Geophysical Fluid Dynamics} 1: 1 463--502.
%
% \item [Hasselmann]K. 1970. Wind--driven inertial
%   oscillations. \textit{Geophysical Fluid Dynamics} 1: 1 463--502.

\bibitem{Hasselmann:1973}
Hasselmann K., T.P. Barnett, E. Bouws, H. Carlson, D.E. Cartwright, K.
Enke, J.A. Ewing, H. Gienapp, D.E. Hasselmann, P. Kruseman,
A. Meerburg, P.  M\"{u}ller, D.J. Olbers, K. Richter, W. Sell, and
H. Walden. 1973. Measurements of wind-wave growth and swell decay
during the Joint North Sea Wave Project
(\textsc{jonswap}). \textit{Erg\"{a}nzungsheft zur Deutschen
  Hydrographischen Zeitschrift Reihe} A($\degrees{8}$) (Nr. 12): 95.
%
% \item [Hasselmann]K., T.P. Barnett, E. Bouws, H. Carlson,
%   D.E. Cartwright, K.  Enke, J.A. Ewing, H. Gienapp, D.E. Hasselmann,
%   P. Kruseman, A. Meerburg, P.  M\"{u}ller, D.J. Olbers, K. Richter,
%   W. Sell, and H. Walden. 1973. Measurements of wind-wave growth and
%   swell decay during the Joint North Sea Wave Project
%   (\textsc{jonswap}). \textit{Erg\"{a}nzungsheft zur Deutschen
%     Hydrographischen Zeitschrift Reihe} A($8^\circ$) (Nr. 12): 95.

\bibitem{Hasselmann:1991}
Hasselmann K., and S. Hasselmann.  1991. On the nonlinear mapping of
an ocean wave spectrum into a synthetic aperture radar image spectrum
and its inversion. \textit{Journal of Geophysical Research} C96
10,713--10,729.
%
% \item [Hasselmann]K., and S. Hasselmann. 1991. On the nonlinear
%   mapping of an ocean wave spectrum into a synthetic aperture radar
%   image spectrum and its inversion. \textit{Journal of Geophysical
%     Research} C96 10,713--10,729.

\bibitem{Heaps:1987}
Heaps N.S., Editor.  1987. \textit{Three-Dimensional Coastal Ocean
  Models}.  Washington DC: American Geophysical Union.
%
% \item [Heaps]N.S., Editor. 1987. \textit{Three-Dimensional Coastal
%   Ocean Models}.  Washington DC: American Geophysical Union.

\bibitem{Hinze:1975}
Hinze J.O.  1975. \textit{Turbulence}. 2nd ed. New York: McGraw-Hill.
%
% \item [Hinze]J.O. 1975. \textit{Turbulence}. 2nd ed. New York:
%   McGraw-Hill.

\bibitem{Hirst:2000} 
Hirst A.C., S.P. O'Farrell, and H.B. Gordon. 2000. Comparison of a
coupled ocean-atmosphere model with and without oceanic eddy-induced
advection.  Part I: Oceanic spinup and control
integration. \textit{Journal of Climate} 13 (1): 139--163.
%
% \item [Hirst]A.C., S.P. O'Farrell, and H.B. Gordon. 2000. Comparison
%   of a coupled ocean-atmosphere model with and without oceanic
%   eddy-induced advection.  Part I: Oceanic spinup and control
%   integration. \textit{Journal of Climate} 13 (1): 139--163.

\bibitem{Hoffman:1975}
Hoffman D., and O.J. Karst.  1975. The theory of the Rayleigh
distribution and some of its applications. \textit{Journal of Ship
  Research} 19 (3): 172--191.
%
% \item [Hoffman]D., and O.J. Karst. 1975. The theory of the Rayleigh
%   distribution and some of its applications. \textit{Journal of Ship
%     Research} 19 (3): 172--191.

\bibitem{Hogg:2001}
Hogg N., J. McWilliams, P. Niiler and J. Price.  2001. Objective
8---To determine the important processes and balances for the dynamics
of the general circulation. In: \textit{2001 U.S. WOCE
  Report}. College Station, Texas, U.S. \textsc{woce} Office: 50--59.
%
% \item [Hogg]N., J. McWilliams, P. Niiler and J. Price. 2001. Objective
%   8---To determine the important processes and balances for the
%   dynamics of the general circulation. In: \textit{2001 U.S. WOCE
%     Report}. College Station, Texas, U.S. \textsc{woce} Office:
%   50--59.

\bibitem{Holloway:1986a}
Holloway G.  1986. Eddies, waves, circulation, and mixing: statistical
geofluid mechanics. \textit{Annual Reviews of Fluid Mechanics} 18:
91--147.
%
% \item [Holloway]G. 1986. Eddies, waves, circulation, and mixing:
%   statistical geofluid mechanics. \textit{Annual Reviews of Fluid
%     Mechanics} 18: 91--147.

\bibitem{Holloway:1986b}
Holloway G.  1986. Estimation of oceanic eddy transports from
satellite altimetry. \textit{Nature} 323 (6085): 243--244.
%
% \item [Holloway]G. 1986. Estimation of oceanic eddy transports from
%   satellite altimetry. \textit{Nature} 323 (6085): 243--244.

\bibitem{Holloway:1994}
Holloway G.  1994. Representing eddy forcing in models. \textsc{woce}
Notes 6 (3): 7--9.
%
% \item [Holloway]G. 1994. Representing eddy forcing in
%   models. \textsc{woce} Notes 6 (3): 7--9.

\bibitem{Horikawa:1988}
Horikawa K.  1988. \textit{Nearshore Dynamics and Coastal Processes}.
Tokyo: University of Tokyo Press.
%
% \item [Horikawa]K. 1988. \textit{Nearshore Dynamics and Coastal
%   Processes}.  Tokyo: University of Tokyo Press.

\bibitem{Houghton:1977}
Houghton J.T.  1977. \textit{The Physics of Atmospheres}. Cambridge:
University Press.
%
% \item [Houghton]J.T. 1977. \textit{The Physics of
%   Atmospheres}. Cambridge: University Press.

\bibitem{Houghton:1996}
Houghton J.T., L.G.M. Filho, B.A. Callander, N. Harris, A. Kattenberg,
and K. Maskell. 1996. \textit{Climate Change 1995: The Science of
  Climate Change}. Cambridge: University Press.
%
% \item [Houghton]J.T., L.G.M. Filho, B.A. Callander, N. Harris,
%   A. Kattenberg, and K. Maskell. 1996. \textit{Climate Change 1995:
%     The Science of Climate Change}. Cambridge: University Press.

\bibitem{Hoyt:1997}
Hoyt D.V., and K.H. Schatten.  1997. \textit{The Role of the Sun in
  Climate Change}.  Oxford: Oxford University Press.
%
% \item [Hoyt]D.V., and K.H. Schatten. 1997. \textit{The Role of the Sun
%   in Climate Change}.  Oxford: Oxford University Press.

\bibitem{Huffman:1995}
Huffman G.J., R.F. Adler, B. Rudolf, U. Schneider, and
P.R. Keehm. 1995.  Global precipitation estimates based on a technique
for combining satellite-based estimates, rain gauge analysis, and
\textsc{nwp} model precipitation information. \textit{Journal of
  Climate} 8: 1284--1295.
%
% \item [Huffman]G.J., R.F. Adler, B. Rudolf, U. Schneider, and
%   P.R. Keehm. 1995.  Global precipitation estimates based on a
%   technique for combining satellite-based estimates, rain gauge
%   analysis, and \textsc{nwp} model precipitation
%   information. \textit{Journal of Climate} 8: 1284--1295.

\bibitem{Huffman:1997}
Huffman G.J., R.F. Adler, P.A. Arkin, A. Chang, R. Ferraro, A. Gruber,
J.  Janowiak, A. McNab, B. Rudolf, and U. Schneider. 1997. The Global
Precipitation Climatology Project (\textsc{gpcp}) combined
precipitation data set.  \textit{Bulletin of the American
  Meteorological Society} 78 (1): 5--20.
%
% \item[Huffman]G.J., R.F. Adler, P.A. Arkin, A. Chang, R. Ferraro,
%   A. Gruber, J.  Janowiak, A. McNab, B. Rudolf, and
%   U. Schneider. 1997. The Global Precipitation Climatology Project
%   (\textsc{gpcp}) combined precipitation data set.  \textit{Bulletin
%     of the American Meteorological Society} 78 (1): 5--20.

\bibitem{Ichiye:1963}
Ichiye T., and J. Petersen.  1963. The anomalous rainfall of the
1957--1958 winter in the equatorial central Pacific arid
area. \textit{Journal of the Meteorological Society of Japan} Series
II, 41: 172--182.
%
% \item [Ichiye]T., and J. Petersen. 1963. The anomalous rainfall of the
%   1957--1958 winter in the equatorial central Pacific arid
%   area. \textit{Journal of the Meteorological Society of Japan} Series
%   II, 41: 172--182.

\bibitem{IHB:1953} 
International Hydrographic Bureau 1953. Limits of oceans and seas,
3rd~ed. Special Report No. 53, Monte Carlo.
%
% \item [International Hydrographic Bureau]1953. Limits of oceans and
%   seas, 3rd ed. Special Report No. 53, Monte Carlo.

\bibitem{IPCC:2007}
Intergovernmental Panel on Climate Change. 2007. \textit{Climate
  Change 2007: The Physical Science Basis. Contribution of Working
  Group I to the Fourth Assessment Report of the Intergovernmental
  Panel on Climate Change}. [Solomon, S., D. Qin, M. Manning, Z. Chen,
  M. Marquis, K.B. Averyt, M. Tignor and H.L. Miller
  (eds.)]. Cambridge University Press, Cambridge, United Kingdom and
New York, NY, USA, 996 pp.
%
% \item [IPCC] Intergovernmental Panel on Climate
%   Change. 2007. \textit{Climate Change 2007: The Physical Science
%     Basis. Contribution of Working Group I to the Fourth Assessment
%     Report of the Intergovernmental Panel on Climate
%     Change}. [Solomon, S., D. Qin, M. Manning, Z. Chen, M. Marquis,
%     K.B. Averyt, M. Tignor and H.L. Miller (eds.)]. Cambridge
%   University Press, Cambridge, United Kingdom and New York, NY, USA,
%   996 pp.

\bibitem{Iselin:1936}
Iselin C.  1936. A study of the circulation of the Western North
Atlantic.  \textit{Physical Oceanography and Meteorology}. 6 (4): 101.
%
% \item [Iselin]C. 1936. A study of the circulation of the Western North
%   Atlantic.  \textit{Physical Oceanography and Meteorology}. 6 (4):
%   101.

\bibitem{Isemer:1987}
Isemer H.J., and L. Hasse.  1987. \textit{The Bunker Climate Atlas of
  the North Atlantic}. Volume 2.  Berlin: Springer-Verlag.
%
% \item [Isemer]H.J., and L. Hasse. 1987. \textit{The Bunker Climate
%   Atlas of the North Atlantic}. Volume 2.  Berlin: Springer-Verlag.

\bibitem{Jackett:1997}
Jackett D.R., and T.J. McDougall.  1997. A neutral density variable
for the world's oceans. \textit{Journal of Physical Oceanography} 27:
237--263.
%
% \item [Jackett]D.R., and T.J. McDougall. 1997. A neutral density
%   variable for the world's oceans. \textit{Journal of Physical
%     Oceanography} 27: 237--263.

\bibitem{Oldenborgh:2005} 
Jan van Oldenborgh G., M.A. Balmaseda, L. Ferranti, T.N. Stockdale,
and D.L.T. Anderson. 2005. Did the ECMWF Seasonal Forecast Model
Outperform Statistical \textsc{enso} Forecast Models over the Last 15
Years? \textit{Journal of Climate} 18 (16): 3240--3249.
%
% \item [Jan van Oldenborgh] G., M.A. Balmaseda, L. Ferranti,
%   T.N. Stockdale, and D.L.T. Anderson. 2005. Did the ECMWF Seasonal
%   Forecast Model Outperform Statistical \textsc{enso} Forecast Models
%   over the Last 15 Years? \textit{Journal of Climate} 18 (16):
%   3240--3249.

\bibitem{Jarosz:2007}
Jarosz E., D.A. Mitchell, D.W. Wang, and W.J. Teague. 2007. Bottom-Up
Determination of Air-Sea Momentum Exchange Under a Major Tropical
Cyclone. \textit{Science} 315 (5819): 1707--1709.
%
% \item [Jarosz]E., D.A. Mitchell, D.W. Wang, and
%   W.J. Teague. 2007. Bottom-Up Determination of Air-Sea Momentum
%   Exchange Under a Major Tropical Cyclone. \textit{Science} 315
%   (5819): 1707--1709.

\bibitem{Jayne:2004}
Jayne S.R., L.C.S. Laurent and S.T. Gille.  2004. Connections between
ocean bottom topography and Earth's climate. \textit{Oceanography} 17
(1): 65--74.
%
% \item [Jayne]S.R., L.C.S. Laurent and S.T. Gille. 2004. Connections
%   between ocean bottom topography and Earth's
%   climate. \textit{Oceanography} 17 (1): 65--74.

\bibitem{Jelesnianski:1992}
Jelesnianski C.P.J., P.C. Chen, and
W.A. Shaffer. 1992. \textsc{slosh}: Sea, lake, and overland surges
from hurricanes. \textsc{noaa} Technical Report \textsc{nws} 48.
%
% \item [Jelesnianski]C.P.J., P.C. Chen, and
%   W.A. Shaffer. 1992. \textsc{slosh}: Sea, lake, and overland surges
%   from hurricanes. \textsc{noaa} Technical Report \textsc{nws} 48.

\bibitem{Jerlov:1976}
Jerlov N.G.  1976. \textit{Marine Optics}. Amsterdam: Elsevier
Scientific Publishing Company.
%
% \item[Jerlov]N.G. 1976. \textit{Marine Optics}. Amsterdam: Elsevier
%   Scientific Publishing Company.

\bibitem{Ji:1996}
Ji M., A. Leetmaa, and V. Kousky.  1996. Coupled model predictions of
\textsc{enso} during the 1980s and the 1990s at the National Centers
for Environmental Prediction. \textit{Journal of Climate} 9 (12):
3105--3120.
%
% \item[Ji]M., A. Leetmaa, and V. Kousky. 1996. Coupled model
%   predictions of \textsc{enso} during the 1980s and the 1990s at the
%   National Centers for Environmental Prediction. \textit{Journal of
%     Climate} 9 (12): 3105--3120.

\bibitem{Ji:1998}
Ji M., D.W. Behringer, and A. Leetmaa.  1998. An improved coupled
model for \textsc{enso} prediction and implications for ocean
initialization. Part II: The coupled model. \textit{Bulletin of the
  American Meteorological Society} 126 (4): 1022--1034.
%
% \item[Ji]M., D.W. Behringer, and A. Leetmaa. 1998. An improved coupled
%   model for \textsc{enso} prediction and implications for ocean
%   initialization. Part II: The coupled model. \textit{Bulletin of the
%     American Meteorological Society} 126 (4): 1022--1034.

\bibitem{Johns:1989}
Johns E., D.R. Watts, and H.T. Rossby.  1989. A test of
  geostrophy in the Gulf Stream. \textit{Journal of Geophysical
    Research} 94 (C3): 3211--3222.
%
% \item [Johns]E., D.R. Watts, and H.T. Rossby. 1989. A test of
%   geostrophy in the Gulf Stream. \textit{Journal of Geophysical
%     Research} 94 (C3): 3211--3222.

\bibitem{Johns:1997}
Johns T.C., R.E. Carnell, J.F. Crossley, J.M. Gregory,
J.F.B. Mitchell, C.A. Senior, S.F.B. Trett, and R.A. Wood. 1997. The
second Hadley Centre coupled ocean-atmosphere GCM: model description,
spinup and validation. \textit{Climate Dynamics} 13 (2): 103--134.
%
% \item [Johns]T.C., R.E. Carnell, J.F. Crossley, J.M. Gregory,
%   J.F.B. Mitchell, C.A. Senior, S.F.B. Trett, and R.A. Wood. 1997. The
%   second Hadley Centre coupled ocean-atmosphere GCM: model
%   description, spinup and validation. \textit{Climate Dynamics} 13
%   (2): 103--134.

\bibitem{Joseph:1958}
Joseph J., and H. Sender.  1958. Uber die horizontale diffusion im
meere.  \textit{Deutsches Hydrographiches Zeitung} 11: 49--77.
%
% \item[Joseph]J., and H. Sender. 1958. Uber die horizontale diffusion
%   im meere.  \textit{Deutsches Hydrographiches Zeitung} 11: 49--77.

\bibitem{Josey:1999}
Josey S.A., E.C. Kent, and P.K. Taylor.  1999. New insights into the
ocean heat budget closure problem from analysis of the \textsc{soc}
air-sea flux climatology. \textit{Journal of Climate} 12: 2856--2880.
%
% \item [Josey]S.A., E.C. Kent, and P.K. Taylor. 1999. New insights into
%   the ocean heat budget closure problem from analysis of the
%   \textsc{soc} air-sea flux climatology. \textit{Journal of Climate}
%   12: 2856--2880.

\bibitem{JPOTS:1981}
Joint Panel on Oceanographic Tables and Standards. 1981. \textit{The
  practical salinity scale 1978 and the international equation of
  state of seawater 1980}. Paris: \textsc{unesco} Technical Papers in
Marine Science 36: 25.
%
% \item [JPOTS]Joint Panel on Oceanographic Tables and
%   Standards. 1981. \textit{The practical salinity scale 1978 and the
%     international equation of state of seawater 1980}. Paris:
%   \textsc{unesco} Technical Papers in Marine Science 36: 25.

\bibitem{JPOTS:1991}
Joint Panel on Oceanographic Tables and
Standards. 1991. \textit{Processing of Oceanographic Station
  Data}. Paris: \textsc{unesco}.
%
% \item [JPOTS]Joint Panel on Oceanographic Tables and
%   Standards. 1991. \textit{Processing of Oceanographic Station
%     Data}. Paris: \textsc{unesco}.

\bibitem{Kalnay:1996}
Kalnay E., M. Kanamitsu, R. Kistler, W. Collins, D. Deaven, L. Gandin,
M. Iredell, S. Saha, G. White, J. Woollen, Y. Zhu, M. Chelliah,
W. Ebisuzaki, W.  Higgins, J. Janowiak, K.C. Mo, C. Ropelewski,
J. Wang, A. Leetmaa, R. Reynolds, R. Jenne, and D. Joseph. 1996. The
\textsc{ncep/ncar} 40--year reanalysis project. \textit{Bulletin
  American Meteorological Society} 77: 437--471.
%
% \item [Kalnay]E., M. Kanamitsu, R. Kistler, W. Collins, D. Deaven,
%   L. Gandin, M. Iredell, S. Saha, G. White, J. Woollen, Y. Zhu,
%   M. Chelliah, W. Ebisuzaki, W.  Higgins, J. Janowiak, K.C. Mo,
%   C. Ropelewski, J. Wang, A. Leetmaa, R. Reynolds, R. Jenne, and
%   D. Joseph. 1996. The \textsc{ncep/ncar} 40--year reanalysis
%   project. \textit{Bulletin American Meteorological Society} 77:
%   437--471.

\bibitem{Kantha:1998}
Kantha L.H.  1998. Tides--A modern perspective. \textit{Marine
  Geodesy} 21: 275--297.
%
% \item[Kantha]L.H. 1998. Tides--A modern perspective. \textit{Marine
%   Geodesy} 21: 275--297.

\bibitem{Kent:1997}
Kent E.C., and P.K. Taylor.  1997. Choice of a Beaufort Scale.
\textit{Journal of Atmospheric and Oceanic Technology} 14 (2):
228--242.
%
% \item [Kent]E.C., and P.K. Taylor. 1997. Choice of a Beaufort Scale.
% \textit{Journal of Atmospheric and Oceanic Technology} 14 (2): 228--242.

\bibitem{Kerr:1998}
Kerr R.A.  1998. Models win big in forecasting El
Ni\~{n}o. \textit{Science} 280 (5363): 522--523.
%
% \item[Kerr]R.A. 1998. Models win big in forecasting El
%   Ni\~{n}o. \textit{Science} 280 (5363): 522--523.

\bibitem{Kerr:2002}
Kerr R.A.  2002. Salt fingers mix the sea. \textit{Science} 295
(5561): 1821.
%
% \item [Kerr]R.A. 2002. Salt fingers mix the sea. \textit{Science} 295
%   (5561): 1821.

\bibitem{Kiehl:1996}
Kiehl J.T., and K.E. Trenberth.  1996. Earth's annual global mean
energy budget. \textit{Bulletin of the American Meteorological
  Society} 78 (2): 197--208.
%
% \item [Kiehl]J.T., and K.E. Trenberth. 1996. Earth's annual global
%   mean energy budget. \textit{Bulletin of the American Meteorological
%     Society} 78 (2): 197--208.

\bibitem{Kilpatrick:2001}
Kilpatrick K.A., G.P. Podesta, and R. Evans.  2001. Overview of the
\textsc{noaa/nasa} advanced very high resolution radiometer Pathfinder
algorithm for sea surface temperature and associated matchup
database. \textit{Journal of Geophysical Research} 106: 9179--9198.
%
% \item [Kilpatrick]K.A., G.P. Podesta, and R. Evans. 2001. Overview of
%   the \textsc{noaa/nasa} advanced very high resolution radiometer
%   Pathfinder algorithm for sea surface temperature and associated
%   matchup database. \textit{Journal of Geophysical Research} 106:
%   9179--9198.

\bibitem{Kistler:2000}
Kistler R.E., E. Kalnay, W. Collins, S. Saha, G. White, J. Woolen, M.
Chelliah, and W. Ebisuzaki. 2000. The \textsc{ncep/ncar} 50-year
reanalysis.  \textit{Bulletin of the American Meteorological Society}
82: 247--267.
%
% \item [Kistler]R.E., E. Kalnay, W. Collins, S. Saha, G. White,
%   J. Woolen, M.  Chelliah, and W. Ebisuzaki. 2000. The
%   \textsc{ncep/ncar} 50-year reanalysis.  \textit{Bulletin of the
%     American Meteorological Society} 82: 247--267.

\bibitem{Komen:1996}
Komen G.J., L. Cavaleri, M. Donelan, K. Hasselmann, S. Hasselmann, and
P.A.E.M. Jans\-sen. 1996. \textit{Dynamics and Modelling of Ocean
  Waves}. 1st paperback ed.  Cambridge: University Press.
%
% \item [Komen]G.J., L. Cavaleri, M. Donelan, K. Hasselmann,
%   S. Hasselmann, and P.A.E.M. Jans\-sen. 1996. \textit{Dynamics and
%     Modelling of Ocean Waves}. 1st paperback ed.  Cambridge:
%   University Press.

\bibitem{Kullenberg:1954}
Kullenberg B.  1954. Vagn Walfrid Ekman 1874--1954. \textit{Journal du
  Conseil international pour l'exploration de la mer} 20 (2):
140--143.
%
% \item [Kullenberg]B. 1954. Vagn Walfrid Ekman
%   1874--1954. \textit{Journal du Conseil international pour
%     l'exploration de la mer} 20 (2): 140--143.

\bibitem{Kumar:1994}
Kumar A., A. Leetmaa, and M. Ji.  1994. Simulations of atmospheric
variability induced by sea surface temperatures and implications for
global warming. \textit{Science} 266 (5185): 632--634.
%
% \item [Kumar]A., A. Leetmaa, and M. Ji. 1994. Simulations of
%   atmospheric variability induced by sea surface temperatures and
%   implications for global warming. \textit{Science} 266 (5185):
%   632--634.

\bibitem{Kundu:1990}
Kundu P.K.  1990. \textit{Fluid Mechanics}. San Diego: Academic Press.
%
% \item [Kundu]P.K. 1990. \textit{Fluid Mechanics}. San Diego: Academic
%   Press.

\bibitem{Kunze:1997}
Kunze E., and J.M. Toole.  1997. Tidally driven vorticity, diurnal
shear, and turbulence atop Fieberling Seamount. \textit{Journal of
  Physical Oceanography} 27 (2): 2,663--2,693.
%
% \item [Kunze]E., and J.M. Toole. 1997. Tidally driven vorticity,
%   diurnal shear, and turbulence atop Fieberling
%   Seamount. \textit{Journal of Physical Oceanography} 27 (2):
%   2,663--2,693.

\bibitem{Lagerloef:1999}
Lagerloef G.S.E., G. Mitchum, R. Lukas, and P. Niiler. 1999. Tropical
Pacific near-surface current estimates from altimeter, wind and
drifter data.  \textit{Journal of Geophysical Research} 104 (C10):
23,313--23,326.
%
% \item [Lagerloef]G.S.E., G. Mitchum, R. Lukas, and
%   P. Niiler. 1999. Tropical Pacific near-surface current estimates
%   from altimeter, wind and drifter data.  \textit{Journal of
%     Geophysical Research} 104 (C10): 23,313--23,326.

\bibitem{Lamb:1945}
Lamb H.  1945. \textit{Hydrodynamics}. 6th, first American
edition. New York: Dover Publications.
%
% \item [Lamb]H. 1945. \textit{Hydrodynamics}. 6th, first American
%   edition. New York: Dover Publications.

\bibitem{Lang:1980}
Lang K.R.  1980. \textit{Astrophysical Formulae: A Compendium for the
  Physicist and Astrophysicist}. 2nd ed.  Berlin: Springer-Verlag.
%
% \item [Lang]K.R. 1980. \textit{Astrophysical Formulae: A Compendium
%   for the Physicist and Astrophysicist}. 2nd ed.  Berlin:
%   Springer-Verlag.

\bibitem{Langer:1999}
Langer J.  1999. Computing in physics: Are we taking it too seriously?
Or not seriously enough? \textit{Physics Today} 52 (7): 11--13.
%
% \item [Langer]J. 1999. Computing in physics: Are we taking it too
%   seriously? Or not seriously enough? \textit{Physics Today} 52 (7):
%   11--13.

\bibitem{Langmuir:1938}
Langmuir I.  1938. Surface motion of water induced by
wind. \textit{Science} 87: 119--123.
%
% \item [Langmuir]I. 1938. Surface motion of water induced by
%   wind. \textit{Science} 87: 119--123.

\bibitem{Larson:2002}
Larson R.  2002. E-Enabled textbooks: Lower cost, higher
functionality. \textit{Syllabus} 15(10): 44.
%
% \item [Larson]R. 2002. E-Enabled textbooks: Lower cost, higher
%   functionality. \textit{Syllabus} 15(10): 44.

\bibitem{Latif:1993}
Latif M., A. Sterl, E. Maier-Reimer, and M.M. Junge.  1993. Structure
and predictability of the El Ni\~{n}o/Southern Oscillation phenomenon
in a coupled ocean-atmosphere model. \textit{Journal of Climate} 6:
700--708.
%
% \item [Latif]M., A. Sterl, E. Maier-Reimer, and M.M. Junge.
%   1993. Structure and predictability of the El Ni\~{n}o/Southern
%   Oscillation phenomenon in a coupled ocean-atmosphere
%   model. \textit{Journal of Climate} 6: 700--708.

\bibitem{Lawrence:1999}
Lawrence M.G., J. Landgraf, P. J\"{o}ckel, and
B. Eaton. 1999. Artifacts in global atmospheric modeling: Two recent
examples. \textit{EOS Transactions American Geophysical Union} 80
(11): 123, 128.
%
% \item [Lawrence]M.G., J. Landgraf, P. J\"{o}ckel, and
%   B. Eaton. 1999. Artifacts in global atmospheric modeling: Two recent
%   examples. \textit{EOS Transactions American Geophysical Union} 80
%   (11): 123, 128.

\bibitem{Lean:1995}
Lean J., J. Beer, and R. Bradley.  1995. Reconstruction of solar
irradiance since 1610: Implications for climate
change. \textit{Geophysical Research Letters} 22 (23): 3195--3198.
%
% \item [Lean]J., J. Beer, and R. Bradley. 1995. Reconstruction of solar
%   irradiance since 1610: Implications for climate
%   change. \textit{Geophysical Research Letters} 22 (23): 3195--3198.

\bibitem{Ledwell:1998}
Ledwell J.R., A.J. Watson and C.S. Law 1998. Mixing of a tracer in the
pycnocline. \textit{Journal of Geophysical Research} 103(C10):
21,499--421,529.
%
% \item [Ledwell]J.R., A.J. Watson and C.S. Law 1998. Mixing of a tracer
%   in the pycnocline. \textit{Journal of Geophysical Research}
%   103(C10): 21,499--421,529.

\bibitem{Leetmaa:1978}
Leetmaa A., and A.F. Bunker.  1978. Updated charts of the mean annual
wind stress, convergences in the Ekman layers and Sverdrup transports
in the North Atlantic. \textit{Journal of Marine Research} 36:
311--322.
%
% \item[Leetmaa]A., and A.F. Bunker. 1978. Updated charts of the mean
%   annual wind stress, convergences in the Ekman layers and Sverdrup
%   transports in the North Atlantic. \textit{Journal of Marine
%     Research} 36: 311--322.

\bibitem{Leetmaa:1981}
Leetmaa A., J.P. McCreary, and D.W. Moore.  1981. Equatorial currents;
observation and theory. In: \textit{Evolution of Physical
  Oceanography}. Edited by B. A. Warren and
C. Wunsch. 184--196. Cambridge: Massachusetts Institute of Technology
Press.
%
% \item[Leetmaa]A., J.P. McCreary, and D.W. Moore. 1981. Equatorial
%   currents; observation and theory. In: \textit{Evolution of Physical
%     Oceanography}. Edited by B. A. Warren and
%   C. Wunsch. 184--196. Cambridge: Massachusetts Institute of
%   Technology Press.

\bibitem{LeProvost:1994}
LeProvost C., M.L. Genco, F. Lyard, P. Vincent, and
P. Canceil. 1994. Spectroscopy of the world ocean tides from a finite
element hydrodynamic model. \textit{Journal Geophysical Research} 99
(C12): 24,777--24,797.
%
% \item [LeProvost]C., M.L. Genco, F. Lyard, P. Vincent, and
%   P. Canceil. 1994. Spectroscopy of the world ocean tides from a
%   finite element hydrodynamic model. \textit{Journal Geophysical
%     Research} 99 (C12): 24,777--24,797.

\bibitem{LeProvost:1995}
LeProvost C., A. F. Bennett and D. E. Cartwright.  1995. Ocean tides
for and from Topex/ Poseidon. \textit{Science} 267 (5198): 639--647.
%
% \item [LeProvost]C., A. F. Bennett and D. E. Cartwright. 1995. Ocean
%   tides for and from Topex/ Poseidon. \textit{Science} 267 (5198):
%   639--647.

\bibitem{LeProvost:2003}
LeProvost C. 2003. Personal communication.

\bibitem{Levitus:1982}
Levitus S.  1982. \textit{Climatological Atlas of the World
  Ocean}. \textsc{noaa} Professional Paper 13.
%
% \item [Levitus]S. 1982. \textit{Climatological Atlas of the World
%   Ocean}. \textsc{noaa} Professional Paper 13.

\bibitem{Levitus:1994}
Levitus S.  1994. \textit{World Ocean Atlas 1994 \textsc{cd-rom} Data
  Set}. \textsc{noaa} National Oceanographic Data Center.
%
% \item [Levitus]S. 1994. \textit{World Ocean Atlas 1994 \textsc{cd-rom}
%   Data Set}. \textsc{noaa} National Oceanographic Data Center.

\bibitem{Lewis:1980}
Lewis E.L.  1980. The Practical Salinity Scale 1978 and its
antecedents.  \textit{IEEE Journal of Oceanic Engineering}
\textsc{oe}-5: 3--8.
%
% \item [Lewis]E.L. 1980. The Practical Salinity Scale 1978 and its
%   antecedents.  \textit{IEEE Journal of Oceanic Engineering}
%   \textsc{oe}-5: 3--8.

\bibitem{List:1966}
List R.J.  1966. \textit{Smithsonian Meteorological Tables}. 6th
ed. Washington DC: The Smithsonian Institution.
%
% \item [List]R.J. 1966. \textit{Smithsonian Meteorological Tables}. 6th
%   ed. Washington DC: The Smithsonian Institution.

\bibitem{Liu:2002}
Liu W.T.  2002. Progress in scatterometer application. \textit{Journal
  of Oceanography} 58: 121--136.
%
% \item [Liu]W.T. 2002. Progress in scatterometer
%   application. \textit{Journal of Oceanography} 58: 121--136.

\bibitem{Longuet-Higgins:1962}
Longuet-Higgins M.S., and O.M. Phillips.  1962. Phase velocity effects
in tertiary wave interactions. \textit{Journal of Fluid Mechanics.} 12
(3): 333--336.
%
% \item [Longuet-Higgins]M.S., and O.M. Phillips. 1962. Phase velocity
%   effects in tertiary wave interactions. \textit{Journal of Fluid
%     Mechanics.} 12 (3): 333--336.

\bibitem{Lynch:1996}
Lynch D.R., J.T.C. Ip, C.E. Naimie, and
F.E. Werner. 1996. Comprehensive coastal circulation model with
application to the Gulf of Maine.  \textit{Continental Shelf Research}
16 (7): 875--906.
%
% \item [Lynch]D.R., J.T.C. Ip, C.E. Naimie, and
%   F.E. Werner. 1996. Comprehensive coastal circulation model with
%   application to the Gulf of Maine.  \textit{Continental Shelf
%     Research} 16 (7): 875--906.

\bibitem{Lynn:1968}
Lynn R.J., and J.L. Reid.  1968. Characteristics and circulation of
deep and abyssal waters. \textit{Deep-Sea Research} 15 (5): 577--598.
%
% \item [Lynn]R.J., and J.L. Reid. 1968. Characteristics and circulation
%   of deep and abyssal waters. \textit{Deep-Sea Research} 15 (5):
%   577--598.

\bibitem{McAvaney:2001}
McAvaney B.J., C. Covey, S. Joussaume, V. Kattsov, A. Kitoh, W. Ogana,
A.J. Pitman, A.J. Weaver, R. A. Wood and Z.-C. Zhao. 2001. Model
Evaluation. In: \textit{Climate Change 2001: The Scientific
  Basis. Contribution of Working Group 1 to the Third Assessment
  Report of the Intergovernmental Panel on Climate Change}.  Editeb by
J.T. Houghton, Y. Ding, D.J. Griggs, N. Noguer, P.J. v. d. Linden, X.
Dai, K. Maskell and C.A. Johnson. Cambridge, University Press: 881.
%
% \item [McAvaney]B.J., C. Covey, S. Joussaume, V. Kattsov, A. Kitoh,
%   W. Ogana, A.J. Pitman, A.J. Weaver, R. A. Wood and
%   Z.-C. Zhao. 2001. Model Evaluation. In: \textit{Climate Change 2001:
%     The Scientific Basis. Contribution of Working Group 1 to the Third
%     Assessment Report of the Intergovernmental Panel on Climate
%     Change}.  Editeb by J.T. Houghton, Y. Ding, D.J. Griggs,
%   N. Noguer, P.J. v. d. Linden, X.  Dai, K. Maskell and
%   C.A. Johnson. Cambridge, University Press: 881.

\bibitem{MacKenzie:1981}
MacKenzie K.V.  1981. Nine-term equation for sound speed in the ocean.
\textit{Journal of the Acoustical Society of America} 70: 807--812.
%
% \item [MacKenzie]K.V. 1981. Nine-term equation for sound speed in the
%   ocean.  \textit{Journal of the Acoustical Society of America} 70:
%   807--812.

\bibitem{McDougall:1987}
McDougall T.J.  1987. Neutral surfaces. \textit{Journal of Physical
  Oceanography} 17 (11): 1950--1964.
%
% \item [McDougall]T.J. 1987. Neutral surfaces. \textit{Journal of
%   Physical Oceanography} 17 (11): 1950--1964.

\bibitem{McDougall:2003}
McDougall T. J. and R. Feistel 2003. What causes the adiabatic lapse
rate? \textit{Deep Sea Research Part I: Oceanographic Research Papers}
50 (12): 1523--1535.
%
% \item [McDougall]T. J. and R. Feistel 2003. What causes the adiabatic
%   lapse rate? \textit{Deep Sea Research Part I: Oceanographic Research
%     Papers} 50 (12): 1523--1535.

\bibitem{McIntyre:1981}
McIntyre M.E.  1981. On the `wave momentum' myth. \textit{Journal of
  Fluid Mechanics} 106: 331--347.
%
% \item [McIntyre]M.E. 1981. On the `wave momentum'
%   myth. \textit{Journal of Fluid Mechanics} 106: 331--347.

\bibitem{McNally:1983}
McNally G.J., W.C. Patzert, A.D. Kirwan, and A.C. Vastano. 1983. The
near-surface circulation of the North Pacific using satellite tracked
drifting buoys. Journal of Geophysical Research 88 (C12):
7,507--7,518.
%
% \item [McNally]G.J., W.C. Patzert, A.D. Kirwan, and
%   A.C. Vastano. 1983. The near-surface circulation of the North
%   Pacific using satellite tracked drifting buoys. Journal of
%   Geophysical Research 88 (C12): 7,507--7,518.

\bibitem{McPhaden:1986}
McPhaden M.J.  1986. The equatorial undercurrent: 100 years of
discovery. \textit{EOS Transansactions of the Amererican Geophysical
  Union} 67 (40): 762--765.
%
% \item [McPhaden]M.J. 1986. The equatorial undercurrent: 100 years of
%   discovery. \textit{EOS Transansactions of the Amererican Geophysical
%     Union} 67 (40): 762--765.

\bibitem{McPhaden:1998}
McPhaden M.J., A.J. Busalacchi, R. Cheney, J.R. Donguy, K.S. Gage,
D. Halpern, M. Ji, P. Julian, G. Meyers, G.T. Mitchum, P.P. Niiler,
J. Picaut, R.W. Reynolds, N. Smith K. Takeuchi. 1998. The Tropical
Ocean-Global Atmosphere (textsc{toa}) observing system: A decade of
progress.  \textit{Journal of Geophysical Research} 103:
14,169--14,240.
%
% \item [McPhaden]M.J., A.J. Busalacchi, R. Cheney, J.R. Donguy,
%   K.S. Gage, D. Halpern, M. Ji, P. Julian, G. Meyers, G.T. Mitchum,
%   P.P. Niiler, J. Picaut, R.W. Reynolds, N. Smith
%   K. Takeuchi. 1998. The Tropical Ocean-Global Atmosphere
%   (textsc{toa}) observing system: A decade of progress.
%   \textit{Journal of Geophysical Research} 103: 14,169--14,240.

\bibitem{McPhaden:1999}
McPhaden M.J.  1999. Genesis and evolution of the 1997-1998 El
Ni\~{n}o. \textit{Science} 283 (5404): 950--954.
%
% \item [McPhaden]M.J. 1999. Genesis and evolution of the 1997-1998 El
%   Ni\~{n}o. \textit{Science} 283 (5404): 950--954.

\bibitem{McPhaden:2006}
McPhaden M.J., S.E. Zebiak, and M.H. Glantz. 2006. \textsc{enso} as an
Integrating Concept in Earth Science. \textit{Science} 314 (5806):
1740--1745.
%
% \item [McPhaden]M.J., S.E. Zebiak, and
%   M.H. Glantz. 2006. \textsc{enso} as an Integrating Concept in Earth
%   Science. \textit{Science} 314 (5806): 1740--1745.

\bibitem{Ma:1994}
Ma X.C., C.K. Shum, R.J. Eanes, and B.D. Tapley. 1994. Determination
of ocean tides from the first year of Topex/Poseidon altimeter
measurements. \textit{Journal of Geophysical Research} 99 (C12):
24,809--24,820.
%
% \item [Ma]X.C., C.K. Shum, R.J. Eanes, and
%   B.D. Tapley. 1994. Determination of ocean tides from the first year
%   of Topex/Poseidon altimeter measurements. \textit{Journal of
%     Geophysical Research} 99 (C12): 24,809--24,820.

\bibitem{Malanotte-Rizzoli:1996}
Malanotte-Rizzoli P., Ed.  1996. \textit{Modern Approaches to Data
  Assimilation in Ocean Modeling}. Amsterdam: Elsevier.
%
% \item [Malanotte-Rizzoli]P., Ed. 1996. \textit{Modern Approaches to
%   Data Assimilation in Ocean Modeling}. Amsterdam: Elsevier.

\bibitem{Maltrud:1998}
Maltrud M.E., R.D. Smith, A.J. Semtner, and R.C. Malone. 1998. Global
eddy-resolving ocean simulations driven by 1985--1995 atmospheric
winds.  \textit{Journal of Geophysical Research} 103 (C13):
30,825--30,852.
%
% \item [Maltrud]M.E., R.D. Smith, A.J. Semtner, and
%   R.C. Malone. 1998. Global eddy-resolving ocean simulations driven by
%   1985--1995 atmospheric winds.  \textit{Journal of Geophysical
%     Research} 103 (C13): 30,825--30,852.

\bibitem{Margules:1906}
Margules M.  1906. Uber Temperaturschichtung in stationarbewegter und
ruhender Luft. \textit{Meteorologische Zeitschrift} 241--244.
%
% \item [Margules]M. 1906. Uber Temperaturschichtung in
%   stationarbewegter und ruhender Luft. \textit{Meteorologische
%     Zeitschrift} 241--244.

\bibitem{Marotzke:1999}
Marotzke J., and J.R. Scott.  1999. Convective mixing and the
thermohaline circulation. \textit{Journal of Physical Oceanography} 29
(11): 2962--2970.
%
% \item [Marotzke]J., and J.R. Scott. 1999. Convective mixing and the
%   thermohaline circulation. \textit{Journal of Physical Oceanography}
%   29 (11): 2962--2970.

\bibitem{Marotzke:2000}
Marotzke J.  2000. Abrupt climate change and thermohaline circulation:
Mechanisms and predictability. \textit{Proceedings National Academy of
  Sciences} 97 (4): 1347--1350.
%
% \item [Marotzke]J. 2000. Abrupt climate change and thermohaline
%   circulation: Mechanisms and predictability. \textit{Proceedings
%     National Academy of Sciences} 97 (4): 1347--1350.

\bibitem{Martrat:2007}
Martrat B., J.O. Grimalt, N.J. Shackleton, L. de Abreu, M.A. Hutterli,
and T.F. Stocker. 2007. Four Climate Cycles of Recurring Deep and
Surface Water Destabilizations on the Iberian Margin. \textit{Science}
317 (5837): 502--507.
%
% \item [Martrat]B., J.O. Grimalt, N.J. Shackleton, L. de Abreu,
%   M.A. Hutterli, and T.F. Stocker. 2007. Four Climate Cycles of
%   Recurring Deep and Surface Water Destabilizations on the Iberian
%   Margin. \textit{Science} 317 (5837): 502--507.

\bibitem{Matthaus:1969} 
Matth\"{a}us W. 1969. Zur entdeckungsgeschichte des \"{A}quatorialen
Unterstroms im Atkantischen Ozean. \textit{Beitrage Meereskunde} 23:
37--70.
%
% \item[Matth\"{a}us]W. 1969. Zur entdeckungsgeschichte des
%   \"{A}quatorialen Unterstroms im Atkantischen Ozean. \textit{Beitrage
%     Meereskunde} 23: 37--70.

\bibitem{Maury:1855}
Maury M.F.  1855. \textit{Physical Geography of the Sea}. Harper.
%
% \item [Maury]M.F. 1855. \textit{Physical Geography of the Sea}.
%   Harper.

\bibitem{May:1998}
May D.A., M.M. Parmenter, D.S. Olszewski, and B.D. McKenzie. 1998.
Operational processing of satellite sea surface temperature retrievals
at the Naval Oceanographic Office. \textit{Bulletin of the American
  Meteorological Society} 79 (3): 397--407.
%
% \item[May]D.A., M.M. Parmenter, D.S. Olszewski, and
%   B.D. McKenzie. 1998.  Operational processing of satellite sea
%   surface temperature retrievals at the Naval Oceanographic
%   Office. \textit{Bulletin of the American Meteorological Society} 79
%   (3): 397--407.

\bibitem{Mellor:1982}
Mellor G.L., and T. Yamada.  1982. Development of a turbulence closure
model for geophysical fluid problems. \textit{Reviews of Geophysics
  and Space Physics} 20 (4): 851--875.
%
% \item [Mellor]G.L., and T. Yamada. 1982. Development of a turbulence
%   closure model for geophysical fluid problems. \textit{Reviews of
%     Geophysics and Space Physics} 20 (4): 851--875.

\bibitem{Mellor:1998}
Mellor G.L.  1998. \textit{User's Guide for a Three-dimensional,
  Primitive equation, Numerical Ocean Model Version 1998}. Princeton,
Princeton University: 41.
%
% \item [Mellor]G.L. 1998. \textit{User's Guide for a Three-dimensional,
%   Primitive equation, Numerical Ocean Model Version 1998}. Princeton,
%   Princeton University: 41.

\bibitem{Menard:1966}
Menard H.W., and S.M. Smith.  1966. Hypsometry of ocean basin
provinces.  \textit{Journal of Geophysical Research} 71: 4305--4325.
%
% \item [Menard]H.W., and S.M. Smith. 1966. Hypsometry of ocean basin
%   provinces.  \textit{Journal of Geophysical Research} 71: 4305--4325.

\bibitem{Mercier:2003}
Mercier H., M. Arhan and J.R.E. Lutjeharm.  2003. Upper-layer
circulation in the eastern Equatorial and South Atlantic Ocean in
January--March 1995. \textit{Deep-Sea Research} 50 (7): 863--887.
%
% \item [Mercier]H., M. Arhan and J.R.E. Lutjeharm. 2003. Upper-layer
%   circulation in the eastern Equatorial and South Atlantic Ocean in
%   January--March 1995. \textit{Deep-Sea Research} 50 (7): 863--887.

\bibitem{Merryfield:1999}
Merryfield W.J., G. Holloway, and A.E. Gargett.  1999. A global ocean
model with double-diffusion mixing. \textit{Journal of Physical
  Oceanography} 29 (6): 1124--1142.
%
% \item [Merryfield]W.J., G. Holloway, and A.E. Gargett.  1999. A global
%   ocean model with double-diffusion mixing. \textit{Journal of
%     Physical Oceanography} 29 (6): 1124--1142.

\bibitem{Miles:1957}
Miles J.W.  1957. On the generation of surface waves by shear flows.
\textit{Journal of Fluid Mechanics}. 3 (2) 185--204.
%
% \item [Miles]J.W. 1957. On the generation of surface waves by shear
%   flows.  \textit{Journal of Fluid Mechanics}. 3 (2) 185--204.

\bibitem{Millero:1973}
Millero F.J., G. Perron, and J.F. Desnoyers.  1973. Heat capacity of
seawater solutions from $\degrees{5}$ to~$\degCent{35}$ and $0.05$ to
$22\ppt$ chlorinity. \textit{Journal of Geophysical Research} 78 (21):
4499--4506.
%
% \item [Millero]F.J., G. Perron, and J.F. Desnoyers. 1973. Heat
%   capacity of seawater solutions from 5\degrees\ to 35\degrees C and
%   0.05 to 22$^\circ/_{\circ\circ}$ chlorinity. \textit{Journal of
%     Geophysical Research} 78 (21): 4499--4506.

\bibitem{Millero:1980}
Millero F.J., C.-T. Chen, A. Bradshaw, and K. Schleicher. 1980. A new
high pressure equation of state for seawater. \textit{Deep-Sea
  Research} 27A: 255--264.
%
% \item[Millero]F.J., C.-T. Chen, A. Bradshaw, and
%   K. Schleicher. 1980. A new high pressure equation of state for
%   seawater. \textit{Deep-Sea Research} 27A: 255--264.

\bibitem{Millero:1981}
Millero F.J., and A. Poisson.  1981. International one-atmosphere
equation of state of seawater.\textit{Deep-Sea Research} 28A (6):
625--629.
%
% \item [Millero]F.J., and A. Poisson. 1981. International
%   one-atmosphere equation of state of seawater.\textit{Deep-Sea
%     Research} 28A (6): 625--629.

\bibitem{Millero:1996}
Millero F.J.  1996. \textit{Chemical Oceanography} (2nd ed). New York,
CRC Press.
%
% \item [Millero]F.J. 1996. \textit{Chemical Oceanography} (2nd ed). New
%   York, CRC Press.

\bibitem{Millero:2008}
Millero F. J., R. Feistel, et al.  2008. The composition of Standard
Seawater and the definition of the Reference-Composition Salinity
Scale. \textit{Deep Sea Research Part I: Oceanographic Research
  Papers} 55 (1): 50--72.
%
% \item [Millero]F. J., R. Feistel, et al. 2008. The composition of
%   Standard Seawater and the definition of the Reference-Composition
%   Salinity Scale. \textit{Deep Sea Research Part I: Oceanographic
%     Research Papers} 55 (1): 50--72.

\bibitem{Montgomery:1962}
Montgomery R.B., and E.D. Stroup.  1962. Equatorial Waters and
Currents at $\degrees{150}$~W in July--August, 1952. Baltimore: The
Johns Hopkins Press.
%
% \item [Montgomery]R.B., and E.D. Stroup. 1962. Equatorial Waters and
%   Currents at 150\degrees W in July--August, 1952. Baltimore: The
%   Johns Hopkins Press.

\bibitem{Morel:1974}
Morel A.  1974. Optical porperties of pure water and pure
seawater. In: \textit{Optical Aspects of Ocean\-ography}. Edited by
N. G. Jerlov and E. S.  Nielson.  1--24. Academic Press.
%
% \item [Morel]A. 1974. Optical porperties of pure water and pure
%   seawater. In: \textit{Optical Aspects of Ocean\-ography}. Edited by
%   N. G. Jerlov and E. S.  Nielson.  1--24. Academic Press.

\bibitem{Moskowitz:1964}
Moskowitz L.  1964. Estimates of the power spectrums for fully
developed seas for wind speeds of 20 to 40 knots. \textit{Journal of
  Geophysical Research} 69 (24): 5161--5179.
%
% \item [Moskowitz]L. 1964. Estimates of the power spectrums for fully
%   developed seas for wind speeds of 20 to 40 knots. \textit{Journal of
%     Geophysical Research} 69 (24): 5161--5179.

\bibitem{Moum:1985}
Moum J.N., and D.R. Caldwell.  1985. Local influences on shear-flow
turbulence in the equatorial ocean. \textit{Science} 230: 315--316.
%
% \item [Moum]J.N., and D.R. Caldwell. 1985. Local influences on
%   shear-flow turbulence in the equatorial ocean. \textit{Science} 230:
%   315--316.

\bibitem{Munk:1950}
Munk W.H.  1950. On the wind-driven ocean circulation. \textit{Journal
  of Meteorology} 7 (2): 79--93.
%
% \item [Munk]W.H. 1950. On the wind-driven ocean
%   circulation. \textit{Journal of Meteorology} 7 (2): 79--93.

\bibitem{Munk:1951}
Munk W.H., and E. Palmen.  1951. A note on the dynamics of the
Antarctic Circumpolar Current. \textit{Tellus} 3: 53--55.
%
% \item [Munk]W.H., and E. Palmen. 1951. A note on the dynamics of the
%   Antarctic Circumpolar Current. \textit{Tellus} 3: 53--55.

\bibitem{Munk:1966a}
Munk W.H.  1966. Abyssal recipes. \textit{Deep-Sea Research} 13:
707--730.
%
% \item [Munk]W.H. 1966. Abyssal recipes. \textit{Deep-Sea Research} 13:
%   707--730.

\bibitem{Munk:1963}
Munk W.H., G.R. Miller, F.E. Snodgrass, and N.F. Barber.  1963.
Directional recording of swell from distant
storms. \textit{Philosophical Transactions Royal Society of London}
255 (1062): 505--584.
%
% \item [Munk]W.H., G.R. Miller, F.E. Snodgrass, and N.F. Barber. 1963.
%   Directional recording of swell from distant
%   storms. \textit{Philosophical Transactions Royal Society of London}
%   255 (1062): 505--584.

\bibitem{Munk:1966b}
Munk W.H., and D.E. Cartwright.  1966. Tidal spectroscopy and
prediction.  \textit{Philosophical Transactions Royal Society London}
Series A. 259 (1105): 533--581.
%
% \item [Munk]W.H., and D.E. Cartwright. 1966. Tidal spectroscopy and
%   prediction.  \textit{Philosophical Transactions Royal Society
%     London} Series A. 259 (1105): 533--581.

\bibitem{Munk:1994}
Munk W.H., R.C. Spindel, A. Baggeroer, and T.G. Birdsall. 1994. The
Heard Island feasibility test. \textit{Journal of the Acoustical
  Society of America} 96 (4): 2330--2342.
%
% \item [Munk]W.H., R.C. Spindel, A. Baggeroer, and
%   T.G. Birdsall. 1994. The Heard Island feasibility
%   test. \textit{Journal of the Acoustical Society of America} 96 (4):
%   2330--2342.

\bibitem{Munk:1995}
Munk W., P. Worcester, and C. Wunsch.  1995. \textit{Ocean Acoustic
  Tomography}.  Cambridge: University Press.
%
% \item [Munk]W., P. Worcester, and C. Wunsch. 1995. \textit{Ocean
%   Acoustic Tomography}.  Cambridge: University Press.

\bibitem{Munk:1998}
Munk W. and C. Wunsch 1998. Abyssal recipes II. \textit{Deep-Sea
  Research} 45: 1976--2009.
%
% \item [Munk]W. and C. Wunsch 1998. Abyssal recipes
%   II. \textit{Deep-Sea Research} 45: 1976--2009.

\bibitem{NAS:1963}
National Academy of Sciences.  1963. \textit{Ocean Wave Spectra:
  Proceedings of a Conference}.  Englewood Cliffs, New Jersey:
Prentice-Hall.
%
% \item [NAS]National Academy of Sciences. 1963. \textit{Ocean Wave
%   Spectra: Proceedings of a Conference}.  Englewood Cliffs, New
%   Jersey: Prentice-Hall.

\bibitem{Neal:1969}
Neal V.T., S. Neshyba, and W. Denner.  1969. Thermal stratification in
the Arctic Ocean. \textit{Science} 166 (3903): 373--374.
%
% \item [Neal]V.T., S. Neshyba, and W. Denner. 1969. Thermal
%   stratification in the Arctic Ocean. \textit{Science} 166 (3903):
%   373--374.

\bibitem{Nerem:2006}
Nerem R.S., E. Leuliette, and A. Cazenave.  2006. Present-day
sea-level change: A review. \textit{Comptes Rendus Geosciences} 338
(14--15): 1077--1083.
%
% \item[Nerem]R.S., E. Leuliette, and A. Cazenave. 2006. Present-day
%   sea-level change: A review. \textit{Comptes Rendus Geosciences} 338
%   (14--15): 1077--1083.

\bibitem{Neumann:1966}
Neumann G., and W.J. Pierson.  1966. \textit{Principles of Physical
  Oceanography}.  New Jersey: Prentice-Hall.
%
% \item [Neumann]G., and W.J. Pierson.  1966. \textit{Principles of
%   Physical Oceanography}.  New Jersey: Prentice-Hall.

\bibitem{Newton:1999}
Newton P.  1999. A manual for planetary management. \textit{Nature}
400 (6743): 399.
%
% \item [Newton]P. 1999. A manual for planetary
%   management. \textit{Nature} 400 (6743): 399.

\bibitem{Niiler:1987}
Niiler P.P., R.E. Davis, and H.J. White.  1987. Water-following
characteristics of a mix\-ed layer drifter. \textit{Deep-Sea Research}
34 (11): 1867--1881.
%
% \item [Niiler]P.P., R.E. Davis, and H.J. White. 1987. Water-following
%   characteristics of a mix\-ed layer drifter. \textit{Deep-Sea
%     Research} 34 (11): 1867--1881.

\bibitem{Niiler:1995}
Niiler P.P., A.S. Sybrandy, K. Bi, P.M. Poulain, and
D. Bitterman. 1995.  Measurement of the water following capability of
holey-sock and \textsc{tristar} drifters. \textit{Deep-Sea Research}
42 (11/12): 1951--1964.
%
% \item [Niiler]P.P., A.S. Sybrandy, K. Bi, P.M. Poulain, and
%   D. Bitterman. 1995.  Measurement of the water following capability
%   of holey-sock and \textsc{tristar} drifters. \textit{Deep-Sea
%     Research} 42 (11/12): 1951--1964.

\bibitem{North:1989}
North G.R. and S. Nakamoto.  1989. Formalism for comparing rain
estimation designs. \textit{Journal of Atmospheric and Oceanic
  Technology}. 6 (6): 985--992.
%
% \item [North]G.R. and S. Nakamoto. 1989. Formalism for comparing rain
%   estimation designs. \textit{Journal of Atmospheric and Oceanic
%     Technology}. 6 (6): 985--992.

\bibitem{Oberhuber:1988}
Oberhuber J.M.  1988. An atlas based on the \textsc{coads} data set:
The budgets of heat, buoyancy and turbulent kinetic energy at the
surface of the global ocean. \textit{Max-Planck-Institut f\"{u}r
  Meteorologie}: Report 15.
%
% \item [Oberhuber]J.M. 1988. An atlas based on the \textsc{coads} data
%   set: The budgets of heat, buoyancy and turbulent kinetic energy at
%   the surface of the global ocean. \textit{Max-Planck-Institut f\"{u}r
%     Meteorologie}: Report 15.

\bibitem{OpenUniversity:1989a}
Open University 1989. \textit{Ocean Circulation}.  Oxford: Pergamon
Press.
%
% \item [Open University]1989a. \textit{Ocean Circulation}.  Oxford:
%   Pergamon Press.

\bibitem{OpenUniversity:1989b}
Open University 1989. \textit{Seawater: Its Composition, Properties
  and Behaviour}.  Oxford: Pergamon Press.
%
% \item[Open University]1989b. \textit{Seawater: Its Composition,
%   Properties and Behaviour}.  Oxford: Pergamon Press.

\bibitem{OpenUniversity:1989c}
Open University 1989. \textit{Waves, Tides and Shallow
  Water--Processes}.  Oxford: Pergamon Press.
%
% \item [Open University]1989c. \textit{Waves, Tides and Shallow
%   Water--Processes}.  Oxford: Pergamon Press.

\bibitem{Oppenheim:1975}
Oppenheim A.V. and R.W. Schafer.  1975. \textit{Digital Signal
  Processing}.  Englewood Cliffs, New Jersey: Prentice-Hall.
%
% \item [Oppenheim]A.V. and R.W. Schafer. 1975. \textit{Digital Signal
%   Processing}.  Englewood Cliffs, New Jersey: Prentice-Hall.

\bibitem{Orsi:1995}
Orsi A.H., T. Whitworth and W.D. Nowlin.  1995. On the meridional
extent and fronts of the Antarctic Circumpolar
Current. \textit{Deep-Sea Research} 42(5): 641--673.
%
% \item [Orsi]A.H., T. Whitworth and W.D. Nowlin. 1995. On the
%   meridional extent and fronts of the Antarctic Circumpolar
%   Current. \textit{Deep-Sea Research} 42(5): 641--673.

\bibitem{Orsi:1999}
Orsi A.H., G.C. Johnson, and J.L. Bullister.  1999. Circulation,
mixing, and production of Antarctic Bottom Water.  \textit{Progress in
  Oceanography} 43 55-109.
%
% \item [Orsi]A.H., G.C. Johnson, and J.L. Bullister. 1999. Circulation,
%   mixing, and production of Antarctic Bottom Water.  \textit{Progress
%     in Oceanography} 43 55-109.

\bibitem{Pacanowski:1981}
Pacanowski R., and S.G.H. Philander.  1981. Parameterization of
vertical mixing in numerical models of tropical
oceans. \textit{Journal of Physical Oceanography} 11: 1443--1451.
%
% \item [Pacanowski]R., and S.G.H. Philander. 1981. Parameterization of
%   vertical mixing in numerical models of tropical
%   oceans. \textit{Journal of Physical Oceanography} 11: 1443--1451.

\bibitem{Pacanowski:1999}
Pacanowski R.C., and S.M. Griffies.  1999 \textit{MOM 3.0 Manual}.
\textsc{Noaa}/Geophysical Fluid Dynamics Laboratory, Princeton.
%
% \item [Pacanowski]R.C., and S.M. Griffies. 1999 \textit{MOM 3.0
%   Manual}.  \textsc{Noaa}/Geophysical Fluid Dynamics Laboratory,
%   Princeton.

\bibitem{Parke:1987}
Parke M.E., R.H. Stewart, D.L. Farless, and D.E. Cartwright. 1987. On
the choice of orbits for an altimetric satellite to study ocean
circulation and tides. \textit{Journal of Geophysical Research} 92:
11,693--11,707.
%
% \item [Parke]M.E., R.H. Stewart, D.L. Farless, and
%   D.E. Cartwright. 1987. On the choice of orbits for an altimetric
%   satellite to study ocean circulation and tides. \textit{Journal of
%     Geophysical Research} 92: 11,693--11,707.

\bibitem{Parker:1994}
Parker R.L.  1994. \textit{Geophysical Inverse Theory}. Princeton:
Princeton University Press.
%
% \item [Parker]R.L. 1994. \textit{Geophysical Inverse
%   Theory}. Princeton: Princeton University Press.

\bibitem{Pedlosky:1987}
Pedlosky J.  1987. \textit{Geophysical Fluid Dynamics}. 2nd ed.
Berlin: Springer Verlag.
%
% \item [Pedlosky]J. 1987. \textit{Geophysical Fluid Dynamics}. 2nd ed.
%   Berlin: Springer Verlag.

\bibitem{Pedlosky:1996}
Pedlosky J.  1996. \textit{Ocean Circulation Theory}.  Berlin:
Springer--Verlag.
%
% \item [Pedlosky]J. 1996. \textit{Ocean Circulation Theory}.  Berlin:
%   Springer--Verlag.

\bibitem{Percival:1993}
Percival D.B., and A.T. Walden.  1993. \textit{Spectral Analysis for
  Physical Applications: Multitaper and Conventional Univariate
  Techniques}.  Cambridge: University Press.
%
% \item [Percival]D.B., and A.T. Walden. 1993. \textit{Spectral Analysis
%   for Physical Applications: Multitaper and Conventional Univariate
%   Techniques}.  Cambridge: University Press.

\bibitem{Philander:1984}
Philander S.G.H., T. Yamagata, and R.C. Pacanowski. 1984. Unstable
air-sea interactions in the tropics. \textit{Journal of Atmospheric
  Research} 41: 604--613.
%
% \item [Philander]S.G.H., T. Yamagata, and
%   R.C. Pacanowski. 1984. Unstable air-sea interactions in the
%   tropics. \textit{Journal of Atmospheric Research} 41: 604--613.

\bibitem{Philander:1990}
Philander S.G.  1990. \textit{El Ni\~{n}o, La Ni\~{n}a, and the
  Southern Oscillation}. Academic Press.
%
% \item [Philander]S.G. 1990. \textit{El Ni\~{n}o, La Ni\~{n}a, and the
%   Southern Oscillation}. Academic Press.

\bibitem{Phillips:1957}
Phillips O.M.  1957. On the generation of waves by turbulent wind.
\textit{Journal of Fluid Mechanics}. 2 (5): 417--445.
%
% \item [Phillips]O.M. 1957. On the generation of waves by turbulent
%   wind.  \textit{Journal of Fluid Mechanics}. 2 (5): 417--445.

\bibitem{Phillips:1960}
Phillips O.M.  1960. On the dynamics of unsteady gravity waves of
finite amplitude.  Part I.  The elementary
interactions. \textit{Journal of Fluid Mechanics} 9 (2): 193--217.
%
% \item [Phillips]O.M. 1960. On the dynamics of unsteady gravity waves
%   of finite amplitude.  Part I.  The elementary
%   interactions. \textit{Journal of Fluid Mechanics} 9 (2): 193--217.

\bibitem{Picaut:1997}
Picaut J., F. Masia, and Y.d. Penhoat.  1997. An advective-reflective
conceptual model for the oscillatory nature of the
ENSO. \textit{Science} 277 (5326): 663--666.
%
% \item [Picaut]J., F. Masia, and Y.d. Penhoat. 1997. An
%   advective-reflective conceptual model for the oscillatory nature of
%   the ENSO. \textit{Science} 277 (5326): 663--666.

\bibitem{Pickard:1990}
Pickard G.L., and W.J. Emery.  1990. \textit{Descriptive Physical
  Oceanography: An Introduction}. 5th enlarged ed. Oxford: Pergamon
Press.
%
% \item [Pickard]G.L., and W.J. Emery. 1990. \textit{Descriptive
%   Physical Oceanography: An Introduction}. 5th enlarged ed. Oxford:
%   Pergamon Press.

\bibitem{Pierson:1964}
Pierson W.J., and L. Moskowitz.  1964. A proposed spectral form for
fully developed wind seas based on the similarity theory of
S.A. Kitaigordskii.  \textit{Journal of Geophysical. Research} 69:
5181--5190.
%
% \item [Pierson]W.J., and L. Moskowitz. 1964. A proposed spectral form
%   for fully developed wind seas based on the similarity theory of
%   S.A. Kitaigordskii.  \textit{Journal of Geophysical. Research} 69:
%   5181--5190.

\bibitem{Pinet:2000}
Pinet P.R.  2000. \textit{Invitation to oceanography}. 2nd Edition.
Sudbury, Massachusetts: Jones and Bartlett Publishers.
%
% \item [Pinet]P.R. 2000. \textit{Invitation to oceanography}. 2nd
%   Edition.  Sudbury, Massachusetts: Jones and Bartlett Publishers.

\bibitem{Polzin:1997}
Polzin K.L., J.M. Toole, J.R. Ledwell, and R.W. Schmitt. 1997. Spatial
variability of turbulent mixing in the abyssal ocean. \textit{Science}
276 (5309): 93--96.
%
% \item [Polzin]K.L., J.M. Toole, J.R. Ledwell, and
%   R.W. Schmitt. 1997. Spatial variability of turbulent mixing in the
%   abyssal ocean. \textit{Science} 276 (5309): 93--96.

\bibitem{Post:2005}
Post D.E. and L.G. Votta.  2005. Computational science demands a new
paradigm. \textit{Physics Today} 58 (1): 35--41.
%
% \item[Post]D.E. and L.G. Votta. 2005. Computational science demands a
%   new paradigm. \textit{Physics Today} 58 (1): 35--41.

\bibitem{Powell:2003}
Powell M. D., P.J. Vickery and T.A. Reinhold.  2003. Reduced drag
coefficient for high wind speeds in tropical cyclones. \textit{Nature}
422 (6929): 279--283.
%
% \item [Powell]M. D., P.J. Vickery and T.A. Reinhold. 2003. Reduced
%   drag coefficient for high wind speeds in tropical
%   cyclones. \textit{Nature} 422 (6929): 279--283.

\bibitem{Press:1992}
Press W.H., S.A. Teukolsky, W.T. Vetterling, and B.P. Flannery. 1992.
\textit{Numerical Recipes in FORTRAN}. 2nd ed.  Cambridge: University
Press.
%
% \item [Press]W.H., S.A. Teukolsky, W.T. Vetterling, and
%   B.P. Flannery. 1992.  \textit{Numerical Recipes in FORTRAN}. 2nd ed.
%   Cambridge: University Press.

\bibitem{Preston-Thomas:1990}
Preston-Thomas H.  1990. The International Temperature Scale of 1990
(\textsc{its}-90). \textit{Metrologia} 27 (1): 3--10.
%
% \item [Preston-Thomas]H. 1990. The International Temperature Scale of
%   1990 (\textsc{its}-90). \textit{Metrologia} 27 (1): 3--10.

\bibitem{Proudman:1916}
Proudman J.  1916. On the motion of solids in a liquid possessing
vorticity. \textit{Proceedings Royal Society (London)} A 92: 408--424
%
% \item [Proudman]J. 1916. On the motion of solids in a liquid
%   possessing vorticity. \textit{Proceedings Royal Society (London)} A
%   92: 408--424

\bibitem{Pugh:1987}
Pugh D.T.  1987. \textit{Tides, Surges, and Mean Sea-Level}.
Chichester: John Wiley.
%
% \item [Pugh]D.T. 1987. \textit{Tides, Surges, and Mean Sea-Level}.
%   Chichester: John Wiley.

\bibitem{Rahmstorf:1995}
Rahmstorf S.  1995. Bifurcations of the Atlantic thermohaline
circulation in response to changes in the hydrological
cycle. \textit{Nature} 378: 145--149.
%
% \item [Rahmstorf]S. 1995. Bifurcations of the Atlantic thermohaline
%   circulation in response to changes in the hydrological
%   cycle. \textit{Nature} 378: 145--149.

\bibitem{Ralph:2000}
Ralph E.A., and P.P. Niiler.  2000. Wind-driven currents in the
tropical Pacific. \textit{Journal of Physical Oceanography} 29 (9):
2121--2129.
%
% \item [Ralph]E.A., and P.P. Niiler. 2000. Wind-driven currents in the
%   tropical Pacific. \textit{Journal of Physical Oceanography} 29 (9):
%   2121--2129.

\bibitem{Ramanathan:1995}
Ramanathan V., B. Subasilar, G.J. Zhang, W. Conant, R.D. Cess,
J.T. Kiehl, H. Grassl, and L. Shi. 1995. Warm pool heat budget
shortwave cloud forcing: A missing physics? \textit{Science} 267
(5197): 499--503.
%
% \item [Ramanathan]V., B. Subasilar, G.J. Zhang, W. Conant, R.D. Cess,
%   J.T. Kiehl, H. Grassl, and L. Shi. 1995. Warm pool heat budget
%   shortwave cloud forcing: A missing physics? \textit{Science} 267
%   (5197): 499--503.

\bibitem{Rasmusson:1982}
Rasmusson E.M., and T.H. Carpenter.  1982. Variations in tropical sea
surface temperature and surface wind fields associated with the
Southern Oscillation/El Ni\~{n}o. \textit{Monthly Weather Review} 110:
354--384.
%
% \item [Rasmusson]E.M., and T.H. Carpenter. 1982. Variations in
%   tropical sea surface temperature and surface wind fields associated
%   with the Southern Oscillation/El Ni\~{n}o. \textit{Monthly Weather
%     Review} 110: 354--384.

\bibitem{Rasmusson:1983}
Rasmusson E.M., and J.M. Wallace.  1983. Meteorological Aspects of the
El Ni\~{n}o/Southern Oscillation. \textit{Science} 222: 1195--1202.
%
% \item [Rasmusson]E.M., and J.M. Wallace. 1983. Meteorological Aspects
%   of the El Ni\~{n}o/Southern Oscillation. \textit{Science} 222:
%   1195--1202.

\bibitem{Reid:1948}
Reid R.O.  1948. The equatorial currents of the eastern Pacific as
maintained by the stress of the wind. \textit{Journal of Marine
  Research} 7 (2): 75--99.
%
% \item [Reid]R.O. 1948. The equatorial currents of the eastern Pacific
%   as maintained by the stress of the wind. \textit{Journal of Marine
%     Research} 7 (2): 75--99.

\bibitem{Reynolds:1883}
Reynolds O.  1883. An experimental investigation of the circumstances
which determine whether the motion of water will be direct or sinuous,
and the law of resistance in parallel channels. \textit{Philosophical
  Transactions, Royal Society London} 174: 935.
%
% \item [Reynolds]O. 1883. An experimental investigation of the
%   circumstances which determine whether the motion of water will be
%   direct or sinuous, and the law of resistance in parallel
%   channels. \textit{Philosophical Transactions, Royal Society London}
%   174: 935.

\bibitem{Reynolds:1993}
Reynolds R.W., and D.C. Marsico.  1993. An improved real-time global
sea surface temperature analysis. \textit{Journal of Climate} 6:
114--119.
%
% \item [Reynolds]R.W., and D.C. Marsico. 1993. An improved real-time
%   global sea surface temperature analysis. \textit{Journal of Climate}
%   6: 114--119.

\bibitem{Reynolds:1994}
Reynolds R.W., and T.M. Smith.  1994. Improved global sea surface
temperature analysis using optimum interpolation. \textit{Journal of
  Climate} 7: 929--948.
%
% \item [Reynolds]R.W., and T.M. Smith. 1994. Improved global sea
%   surface temperature analysis using optimum
%   interpolation. \textit{Journal of Climate} 7: 929--948.

\bibitem{Reynolds:1995}
Reynolds R.W., and T.M. Smith.  1995. A high-resolution global sea
surface climatology. \textit{Journal of Climate} 8 (6): 1571--1583.
%
% \item [Reynolds]R.W., and T.M. Smith. 1995. A high-resolution global
%   sea surface climatology. \textit{Journal of Climate} 8 (6):
%   1571--1583.

\bibitem{Reynolds:2002}
Reynolds R.W., N.A. Rayner, T. M. Smith, D. C. Stokes,
W. Wang. 2002. An improved in situ and satellite SST analysis for
climate. \textit{Journal of Climate} 15: 1609--1625.
%
% \item [Reynolds]R.W., N.A. Rayner, T. M. Smith, D. C. Stokes,
%   W. Wang. 2002. An improved in situ and satellite SST analysis for
%   climate. \textit{Journal of Climate} 15: 1609--1625.

\bibitem{Rhines:1984}
Rhines P.B.  1984. Notes on the general circulation of the ocean. In:
\textit{A Celebration in Geophysics and
  Oceanography--1982}. 83--86. Scripps Institution of Oceanography.
%
% \item [Rhines]P.B. 1984. Notes on the general circulation of the
%   ocean. In: \textit{A Celebration in Geophysics and
%     Oceanography--1982}. 83--86. Scripps Institution of Oceanography.

\bibitem{Richardson:1961}
Richardson E.G.  1961. \textit{Dynamics of Real Fluids}. 2nd
ed. London: Edward Arnolds.
%
% \item [Richardson]E.G. 1961. \textit{Dynamics of Real Fluids}. 2nd
%   ed. London: Edward Arnolds.

\bibitem{Richardson:1981}
Richardson P.L.  1981. Eddy kinetic energy in the North Atlantic from
surface drifters. \textit{Journal of Geophysical Research}. 88 (C7):
4355--4367.
%
% \item [Richardson]P.L. 1981. Eddy kinetic energy in the North Atlantic
% from surface drifters. \textit{Journal of Geophysical Research}. 88 (C7): 4355--4367.

\bibitem{Richardson:1993}
Richardson P.L.  1993. Tracking Ocean Eddies. \textit{American
  Scientist} 81: 261--271.
%
% \item [Richardson]P.L. 1993. Tracking Ocean Eddies. \textit{American
%   Scientist} 81: 261--271.

\bibitem{Richardson:2008}
Richardson P. L.  2008. On the history of meridional overturning
circulation schematic diagrams. \textit{Progress In Oceanography} 76
(4): 466--486.
%
% \item [Richardson]P. L. 2008. On the history of meridional overturning
%   circulation schematic diagrams. \textit{Progress In Oceanography} 76
%   (4): 466--486.

\bibitem{Ring Group:1981}
Ring Group (R.H. Backus, G.R. Flierl, D.R. Kester, D.B. Olson,
P.L. Richardson, A.C. Vastano, P.H. Wiebe, and
J.H. Wormuth). 1981. Gulf Stream cold-core rings: Their physics,
chemistry, and biology. \textit{Science} 212 (4499): 1091--1100.
%
% \item [Ring Group]R.H. Backus, G.R. Flierl, D.R. Kester, D.B. Olson,
%   P.L. Richardson, A.C. Vastano, P.H. Wiebe, and
%   J.H. Wormuth. 1981. Gulf Stream cold-core rings: Their physics,
%   chemistry, and biology. \textit{Science} 212 (4499): 1091--1100.

\bibitem{Rintoul:1991}
Rintoul S.R., and C. Wunsch.  1991. Mass, heat, oxygen and nutrient
fluxes and budgets in the North Atlantic Ocean. \textit{Deep-Sea
  Research} 38 (Supplement 1): S355--S377.
%
% \item [Rintoul]S.R., and C. Wunsch. 1991. Mass, heat, oxygen and
%   nutrient fluxes and budgets in the North Atlantic
%   Ocean. \textit{Deep-Sea Research} 38 (Supplement 1): S355--S377.

\bibitem{Riser:2008}
Riser S. C., L. Ren, et al.  2008. Salinity in
  ARGO. \textit{Oceanography} 21 (1): 56--67.
%
% \item [Riser]S. C., L. Ren, et al. 2008. Salinity in
%   ARGO. \textit{Oceanography} 21 (1): 56--67.

\bibitem{Robinson:1989}
Robinson A.R., S.M. Glenn, M.A. Spall, L.J. Walstad, G.M. Gardner, and
W.G. Leslie. 1989. Forecasting Gulf Stream meanders and
rings. \textit{EOS Transactions American Geophysical Union} 70: (45).
%
% \item [Robinson]A.R., S.M. Glenn, M.A. Spall, L.J. Walstad,
%   G.M. Gardner, and W.G. Leslie. 1989. Forecasting Gulf Stream
%   meanders and rings. \textit{EOS Transactions American Geophysical
%     Union} 70: (45).

\bibitem{Roed:1995}
Roed L.P., B. Hackett, B. Gjevik, and L.I. Eide.  1995. A review of
the Metocean Modeling Project (\textsc{mompop}) Part 1: Model
comparison study. In: \textit{Quantitative Skill Assessment for
  Coastal Ocean Models}. Edited by D. R. Lynch and
A. M. Davies. 285--305. Washington DC: American Geophysical Union.
%
% \item [Roed]L.P., B. Hackett, B. Gjevik, and L.I. Eide. 1995. A review
%   of the Metocean Modeling Project (\textsc{mompop}) Part 1: Model
%   comparison study. In: \textit{Quantitative Skill Assessment for
%     Coastal Ocean Models}. Edited by D. R. Lynch and
%   A. M. Davies. 285--305. Washington DC: American Geophysical Union.

\bibitem{Ropelewski:1987}
Ropelewski C.F., and M.S. Halpert.  1987. Global and regional
precipitation associated with El Ni\~{n}o/Southern
Oscillation. \textit{Monthly Weather Review} 115: 1606--1626.
%
% \item [Ropelewski]C.F., and M.S. Halpert. 1987. Global and regional
%   precipitation associated with El Ni\~{n}o/Southern
%   Oscillation. \textit{Monthly Weather Review} 115: 1606--1626.

\bibitem{Rossby:1936}
Rossby C.C.  1936. Dynamics of steady ocean currents in the light of
experimental fluid mechanics. \textit{Papers in Physical Oceanography
  and Meteorology, Massachusetts Institute of Technology and Woods
  Hole Oceanographic Institution}. 5(1): 43.
%
% \item [Rossby]C.C. 1936. Dynamics of steady ocean currents in the
%   light of experimental fluid mechanics. \textit{Papers in Physical
%     Oceanography and Meteorology, Massachusetts Institute of
%     Technology and Woods Hole Oceanographic Institution}. 5(1): 43.

\bibitem{Rossow:1991}
Rossow W.B. and R.A. Schiffer.  1991. \textsc{Isccp} Cloud Data
Products. \textit{Bulletin of the American Meteorology Society}, 72
(1): 2--20.
%
% \item [Rossow]W.B. and R.A. Schiffer. 1991. \textsc{Isccp} Cloud Data
%   Products. \textit{Bulletin of the American Meteorology Society}, 72
%   (1): 2--20.

\bibitem{Rudnick:2003}
Rudnick , D.L., T.J. Boyd, R.E. Brainard, G.S. Carter, G.D. Egbert,
M.C. Gregg, P.E. Holloway, J.M. Klymak, E. Kunze, C.M. Lee,
M.D. Levine, D.S. Luther, J.P. Martin, M.A. Merrifield, J.N. Moum,
J.D. Nash, R. Pinkel, L. Rainville, T.B. Sanford. 2003. From Tides to
Mixing Along the Hawaiian Ridge. \textit{Science} 301 (5631):
355--357.
%
% \item [Rudnick], D.L., T.J. Boyd, R.E. Brainard, G.S. Carter,
%   G.D. Egbert, M.C. Gregg, P.E. Holloway, J.M. Klymak, E. Kunze,
%   C.M. Lee, M.D. Levine, D.S. Luther, J.P. Martin, M.A. Merrifield,
%   J.N. Moum, J.D. Nash, R. Pinkel, L. Rainville,
%   T.B. Sanford. 2003. From Tides to Mixing Along the Hawaiian
%   Ridge. \textit{Science} 301 (5631): 355--357.

\bibitem{Sabine:2004}
Sabine C.L., R.A. Feely, N. Gruber, R.M. Key, K. Lee, J.L. Bullister,
R. Wanninkhof, C.S. Wong, D.W.R. Wallace, B. Tilbrook, F.J. Millero,
T.-H. Peng, A. Kozyr, T. Ono and A.F. Rios. 2004. The Oceanic Sink for
Anthropogenic \COtwo. \textit{Science} 305 (5682): 367--371.
%
% \item [Sabine]C.L., R.A. Feely, N. Gruber, R.M. Key, K. Lee,
%   J.L. Bullister, R. Wanninkhof, C.S. Wong, D.W.R. Wallace,
%   B. Tilbrook, F.J. Millero, T.-H. Peng, A. Kozyr, T. Ono and
%   A.F. Rios. 2004. The Oceanic Sink for Anthropogenic
%   CO$_2$. \textit{Science} 305 (5682): 367--371.

\bibitem{Sandwell:2001}
Sandwell D.T., and W.H.F. Smith.  2001. Bathymetric Estimation. In:
\textit{Satellite Altimetry and Earth Sciences}. Edited by L.-L. Fu
and A. Cazanave. 441--457. San Diego: Academic Press.
%
% \item [Sandwell]D.T., and W.H.F. Smith. 2001. Bathymetric
%   Estimation. In: \textit{Satellite Altimetry and Earth
%     Sciences}. Edited by L.-L. Fu and A. Cazanave. 441--457. San
%   Diego: Academic Press.

\bibitem{Satake:1996}
Satake K., K. Shimazaki, Y. Tsuji, and K. Ueda.  1996. Time and size
of a giant earthquake in Cascadia inferred from Japanese tsunami
records of January 1700. \textit{Nature} 379 (6562): 246--249.
%
% \item [Satake]K., K. Shimazaki, Y. Tsuji, and K. Ueda. 1996. Time and
%   size of a giant earthquake in Cascadia inferred from Japanese
%   tsunami records of January 1700. \textit{Nature} 379 (6562):
%   246--249.

\bibitem{Saunders:1976}
Saunders P.M. and N. P. Fofonoff.  1976. Conversion of pressure to
depth in the ocean. \textit{Deep-Sea Research} 23: 109--111.
%
% \item [Saunders]P.M. and N. P. Fofonoff. 1976. Conversion of pressure
%   to depth in the ocean. \textit{Deep-Sea Research} 23: 109--111.

\bibitem{Saunders:1986}
Saunders P.M.  1986. The accuracy of measurements of salinity, oxygen
and temperature in the deep ocean. \textit{Journal of Physical
  Oceanography} 16 (1): 189--195.
%
% \item [Saunders]P.M. 1986. The accuracy of measurements of salinity,
%   oxygen and temperature in the deep ocean. \textit{Journal of
%     Physical Oceanography} 16 (1): 189--195.

\bibitem{Schmitt:1987}
Schmitt R.W., H. Perkins, J.D. Boyd, and M.C. Stalcup. 1987. C-SALT:
An investigation of the thermohaline staircase in the western tropical
North Atlantic. \textit{Deep-Sea Research} 34 (10): 1655--1665.
%
% \item [Schmitt]R.W., H. Perkins, J.D. Boyd, and
%   M.C. Stalcup. 1987. C-SALT: An investigation of the thermohaline
%   staircase in the western tropical North Atlantic. \textit{Deep-Sea
%     Research} 34 (10): 1655--1665.

\bibitem{Schmitt:1989}
Schmitt R.W., P.S. Bogden, and C.E. Dorman.  1989. Evaporation minus
precipitation and density fluxes for the North
Atlantic. \textit{Journal of Physical Oceanography} 19: 1208--1221.
%
% \item [Schmitt]R.W., P.S. Bogden, and C.E. Dorman. 1989. Evaporation
%   minus precipitation and density fluxes for the North
%   Atlantic. \textit{Journal of Physical Oceanography} 19: 1208--1221.

\bibitem{Schmitt:1994}
Schmitt R.W.  1994. The ocean freshwater cycle. \textsc{jsc} Ocean
Observing System Development Panel, Texas A\&M University, College
Station, Texas: 40.
%
% \item [Schmitt]R.W. 1994. The ocean freshwater cycle. \textsc{jsc}
%   Ocean Observing System Development Panel, Texas A\&M University,
%   College Station, Texas: 40.

\bibitem{Schmitz:1996}
Schmitz W.J.  1996. On the World Ocean Circulation: Volume I. Some
Global Features/ North Atlantic Circulation. Woods Hole Oceanographic
Institution, Technical Report \textsc{whoi}--96--03.
%
% \item [Schmitz]W.J. 1996. On the World Ocean Circulation: Volume
%   I. Some Global Features/ North Atlantic Circulation. Woods Hole
%   Oceanographic Institution, Technical Report \textsc{whoi}--96--03.

\bibitem{Schubert:1993}
Schubert S.D., R.B. Rood, and J. Pfaendtner.  1993. An assimilated
dataset for Earth science applications. \textit{Bulletin American
  Meteorological Society} 74 (12): 2331--2342.
%
% \item [Schubert]S.D., R.B. Rood, and J. Pfaendtner. 1993. An
%   assimilated dataset for Earth science applications. \textit{Bulletin
%     American Meteorological Society} 74 (12): 2331--2342.

\bibitem{Selby:1975}
Selby J.E.A., and R.A. McClatchey.  1975. Atmospheric transmittance
from~$0.25$ to~$28.5\mum$: Computer code \textsc{lowtran} 3. Air Force
Cambridge Research Laboratories, Optical Physics Laboratory Technical
Report TR--75--0255.
%
% \item [Selby]J.E.A., and R.A. McClatchey. 1975. Atmospheric
%   transmittance from 0.25 to 28.5 $\mu$m: Computer code
%   \textsc{lowtran} 3. Air Force Cambridge Research Laboratories,
%   Optical Physics Laboratory Technical Report TR--75--0255.

\bibitem{Service:1996}
Service R.F.  1996. Rock chemistry traces ancient
traders. \textit{Science} 274 (5295): 2012--2013.
%
% \item [Service]R.F. 1996. Rock chemistry traces ancient
%   traders. \textit{Science} 274 (5295): 2012--2013.

\bibitem{Sette:1960}
Sette O.E., and J.D. Isaacs.  1960. Symposium on ``The Changing
Pacific Ocean in 1957 and 1958''. California Cooperative Oceanic
Fisheries Investigations Reports VII: 13--217.
%
% \item[Sette]O.E., and J.D. Isaacs. 1960. Symposium on ``The Changing
%   Pacific Ocean in 1957 and 1958''. California Cooperative Oceanic
%   Fisheries Investigations Reports VII: 13--217.

\bibitem{Shamos:1995}
Shamos M.H.  1995. \textit{The Myth of Scientific Literacy}. New
Brunswick: Rutger University Press.
%
% \item [Shamos]M.H. 1995. \textit{The Myth of Scientific Literacy}. New
%   Brunswick: Rutger University Press.

\bibitem{Shchepetkin:2004}
Shchepetkin A. F. and J.C. McWilliams.  2004. The Regional Oceanic
Modeling System: A split-explicit, free-surface,
topography-following-coordinate ocean model. \textit{Ocean Modelling}
9: 347--404.
%
% \item [Shchepetkin]A. F. and J.C. McWilliams. 2004. The Regional
%   Oceanic Modeling System: A split-explicit, free-surface,
%   topography-following-coordinate ocean model. \textit{Ocean
%     Modelling} 9: 347--404.

\bibitem{Shepard:1950}
Shepard F.P., G.A. MacDonald and D.C. Cox.  1950. The tsunami of April
1, 1946. \textit{Bulletin of the Scripps Institution of Oceanography}
5(6): 391--528.
%
% \item [Shepard]F.P., G.A. MacDonald and D.C. Cox. 1950. The tsunami of
%   April 1, 1946. \textit{Bulletin of the Scripps Institution of
%     Oceanography} 5(6): 391--528.

\bibitem{Shepard:1963}
Shepard F.P.  1963. \textit{Submarine Geology}. 2nd ed. New York:
Harper and Row.
%
% \item [Shepard]F.P. 1963. \textit{Submarine Geology}. 2nd ed. New
%   York: Harper and Row.

\bibitem{Slingo:1995}
Slingo J.M., K.R. Sperber, J.S. Boyle, J.-P. Ceron, M. Dix, B. Dugas,
W. Ebisuzaki, J. Fyfe, D. Gregory, J.-F. Gueremy, J. Hack,
A. Harzallah, P. Inness, A. Kitoh, W.K.-M. Lau, B. McAvaney,
R. Madden, A. Matthews, T.N. Palmer, C.-K. Park, D. Randall, and
N. Renno. 1995. Atmospheric Model Intercomparison Project
(\textsc{amip}): Intraseasonal Oscillations in 15 Atmospheric General
Circulation Models (Results From an \textsc{aimp} Diagnostics
Subproject). World Meteorological Organization/World Climate Research
Programme, WCRP--88 (WMO/TD No. 661).
%
% \item [Slingo]J.M., K.R. Sperber, J.S. Boyle, J.-P. Ceron, M. Dix,
%   B. Dugas, W. Ebisuzaki, J. Fyfe, D. Gregory, J.-F. Gueremy, J. Hack,
%   A. Harzallah, P. Inness, A. Kitoh, W.K.-M. Lau, B. McAvaney,
%   R. Madden, A. Matthews, T.N. Palmer, C.-K. Park, D. Randall, and
%   N. Renno. 1995. Atmospheric Model Intercomparison Project
%   (\textsc{amip}): Intraseasonal Oscillations in 15 Atmospheric
%   General Circulation Models (Results From an \textsc{aimp}
%   Diagnostics Subproject). World Meteorological Organization/World
%   Climate Research Programme, WCRP--88 (WMO/TD No. 661).

\bibitem{Slutz:1985}
Slutz R.J., S.J. Lubker, J.D. Hiscox, S.D. Woodruff, R.L. Jenne,
D.H. Joseph, P.M. Steurer, and J.D. Elms. 1985: Comprehensive
Ocean-Atmosphere Data Set; Release 1. \textsc{noaa} Environmental
Research Laboratories, Climate Research Program, Boulder, Colorado:,
268. (NTIS PB86--105723).
%
% \item [Slutz]R.J., S.J. Lubker, J.D. Hiscox, S.D. Woodruff,
%   R.L. Jenne, D.H. Joseph, P.M. Steurer, and J.D. Elms. 1985:
%   Comprehensive Ocean-Atmosphere Data Set; Release 1. \textsc{noaa}
%   Environmental Research Laboratories, Climate Research Program,
%   Boulder, Colorado:, 268. (NTIS PB86--105723).

\bibitem{Smagorinski:1963}
Smagorinski J.  1963. General circulation experiments with primitive
equations I. The basic experiment. \textit{Monthly Weather Review} 91:
99--164.
%
% \item [Smagorinski]J. 1963. General circulation experiments with
%   primitive equations I. The basic experiment. \textit{Monthly Weather
%     Review} 91: 99--164.

\bibitem{Smith:2000}
Smith R.D., M.E. Maltrud, F.O. Bryan and M.W. Hecht. 2000. Numerical
simulation of the North Atlantic ocean
at~$\degrees{1/10}$. \textit{Journal of Physical Oceanography} 30 (7):
1532--1561.
%
% \item [Smith]R.D., M.E. Maltrud, F.O. Bryan and
%   M.W. Hecht. 2000. Numerical simulation of the North Atlantic ocean
%   at 1/10\degrees. \textit{Journal of Physical Oceanography} 30 (7):
%   1532--1561.

\bibitem{Smith:1980}
Smith S.D.  1980. Wind stress and heat flux over the ocean in gale
force winds. \textit{Journal of Physical Oceanography} 10: 709-726.
%
% \item [Smith]S.D. 1980. Wind stress and heat flux over the ocean in
%   gale force winds. \textit{Journal of Physical Oceanography} 10:
%   709-726.

\bibitem{Smith:1988}
Smith S.D.  1988. Coefficients for sea surface wind stress, heat flux
and wind profiles as a function of wind speed and
temperature. \textit{Journal of Geophysical Research} 93:
15,467--15,472.
%
% \item [Smith]S.D. 1988. Coefficients for sea surface wind stress, heat
%   flux and wind profiles as a function of wind speed and
%   temperature. \textit{Journal of Geophysical Research} 93:
%   15,467--15,472.

\bibitem{Smith:2002}
Smith T.M., T.R. Karl and R.W. Reynolds.  2002. How accurate are
climate simulations? \textit{Science} 296 (5567): 483--484.
%
% \item [Smith]T.M., T.R. Karl and R.W. Reynolds. 2002. How accurate are
%   climate simulations? \textit{Science} 296 (5567): 483--484.

\bibitem{Smith:2004}
Smith T.M., and R.W. Reynolds.  2004. Improved extended reconstruction
of \textsc{sst} (1854--1997). \textit{Journal of Climate} 17 (6):
2466--2477.
%
% \item [Smith]T.M., and R.W. Reynolds. 2004. Improved extended
%   reconstruction of \textsc{sst} (1854--1997). \textit{Journal of
%     Climate} 17 (6): 2466--2477.

\bibitem{Smith:1994}
Smith W.H.F., and D.T. Sandwell.  1994. Bathymetric prediction from
dense satellite altimetry and sparse shipboard
bathymetry. \textit{Journal of Geophysical Research} 99 (B11):
21,803--21,824.
%
% \item [Smith]W.H.F., and D.T. Sandwell. 1994. Bathymetric prediction
%   from dense satellite altimetry and sparse shipboard
%   bathymetry. \textit{Journal of Geophysical Research} 99 (B11):
%   21,803--21,824.

\bibitem{Smith:1997}
Smith W.H.F. and D.T. Sandwell 1997. Global sea floor topography from
satellite altimetry and ship depth soundings. \textit{Science} 277
(5334): 1956--1962.
%
% \item [Smith]W.H.F. and D.T. Sandwell 1997. Global sea floor
%   topography from satellite altimetry and ship depth
%   soundings. \textit{Science} 277 (5334): 1956--1962.

\bibitem{Snodgrass:1964}
Snodgrass F.E.  1964. Precision digital tide gauge. \textit{Science}
146 (3641): 198--208.
%
% \item[Snodgrass]F.E. 1964. Precision digital tide
%   gauge. \textit{Science} 146 (3641): 198--208.

\bibitem{Soulen:1997}
Soulen R.J., and W.E. Fogle.  1997. Temperature scales below 1
kelvin. \textit{Physics Today} 50 (8 Part 1): 36--42.
%
% \item [Soulen]R.J., and W.E. Fogle. 1997. Temperature scales below 1
%   kelvin. \textit{Physics Today} 50 (8 Part 1): 36--42.

\bibitem{Stammer:1996}
Stammer D., R. Tokmakian, A. Semtner, and C. Wunsch.  1996. How well
does a $\degrees{1/4}$~global circulation model simulate large-scale
oceanic observations? \textit{Journal of Geophysical Research} 101
(C10): 25,779--25,811.
%
% \item [Stammer]D., R. Tokmakian, A. Semtner, and C. Wunsch. 1996. How
%   well does a 1/4\degrees\ global circulation model simulate
%   large-scale oceanic observations? \textit{Journal of Geophysical
%     Research} 101 (C10): 25,779--25,811.

\bibitem{Starr:1968}
Starr V.P.  1968. \textit{Physics of Negative Viscosity Phenomena}.
New York: McGraw-Hill.
%
% \item [Starr]V.P. 1968. \textit{Physics of Negative Viscosity
%   Phenomena}.  New York: McGraw-Hill.

\bibitem{Steig:2006}
Steig E.J.  2006. Climate change: The south-north
connection. \textit{Nature} 444 (7116): 152--153.
%
% \item [Steig]E.J. 2006. Climate change: The south-north
%   connection. \textit{Nature} 444 (7116): 152--153.

\bibitem{Stern:1960}
Stern M.E.  1960. The `salt fountain' and thermohaline
convection. \textit{Tellus} 12: 172--175.
%
% \item [Stern]M.E. 1960. The `salt fountain' and thermohaline
%   convection. \textit{Tellus} 12: 172--175.

\bibitem{Stewart:1992}
Stewart I.  1992. Warning---handle with care! \textit{Nature}
\textbf{355}: 16--17.
%
% \item [Stewart]I. 1992. Warning---handle with care! \textit{Nature}
%   \textbf{355}: 16--17.

\bibitem{Stewart:1980}
Stewart R.H.  1980. Ocean wave measurement techniques. In: \textit{Air
  Sea Interaction, Instruments and Methods}. Edited by L. H. F. Dobson
and R. Davis.  447--470. New York: Plenum Press.
%
% \item [Stewart]R.H. 1980. Ocean wave measurement techniques. In:
%   \textit{Air Sea Interaction, Instruments and Methods}. Edited by
%   L. H. F. Dobson and R. Davis.  447--470. New York: Plenum Press.

\bibitem{Stewart:1985}
Stewart R.H.  1985. \textit{Methods of Satellite
  Oceanography}. University of California Press.
%
% \item [Stewart]R.H. 1985. \textit{Methods of Satellite
%   Oceanography}. University of California Press.

\bibitem{Stewart:1995}
Stewart R.H.  1995. Predictability of Texas Rainfall Patterns on Time
Scales of Six to Twelve Months: A Review. In: \textit{The Changing
  Climate of Texas: Predictability and Implications for the Future}
Edited by J. Norwine, J.R.  Giardino, G.R. North and
J.B. Valdes. College Station, Texas: Texas A\&M University. 38--47
%
% \item [Stewart]R.H. 1995. Predictability of Texas Rainfall Patterns on
%   Time Scales of Six to Twelve Months: A Review. In: \textit{The
%     Changing Climate of Texas: Predictability and Implications for the
%     Future} Edited by J. Norwine, J.R.  Giardino, G.R. North and
%   J.B. Valdes. College Station, Texas: Texas A\&M University. 38--47

\bibitem{Stocker:2000}
Stocker T.F., and O. Marchal.  2000. Abrupt climate change in the
computer: Is it real? \textit{Proceedings National Academy of
  Sciences} 97 (4): 1362--1365.
%
% \item [Stocker]T.F., and O. Marchal. 2000. Abrupt climate change in
%   the computer: Is it real? \textit{Proceedings National Academy of
%     Sciences} 97 (4): 1362--1365.

\bibitem{Stokes:1847}
Stokes G.G.  1847. On the theory of oscillatory
waves. \textit{Cambridge Transactions} 8: 441--473.
%
% \item [Stokes]G.G. 1847. On the theory of oscillatory
%   waves. \textit{Cambridge Transactions} 8: 441--473.

\bibitem{Stommel:1948}
Stommel H.  1948. The westward intensification of wind-driven ocean
currents. \textit{Transactions, American Geophysical Union} 29 (2):
202--206.
%
% \item [Stommel]H. 1948. The westward intensification of wind-driven
%   ocean currents. \textit{Transactions, American Geophysical Union} 29
%   (2): 202--206.

\bibitem{Stommel:1958a}
Stommel H.  1958. The abyssal circulation. \textit{Deep-Sea
  Research} 5 (1): 80--82.
%
% \item[Stommel]H. 1958. The abyssal circulation. \textit{Deep-Sea
%   Research} 5 (1): 80--82.

\bibitem{Stommel:1958b}
Stommel H., A.B. Arons, and A.J. Faller.  1958. Some examples of
stationary flow patterns in bounded basins. \textit{Tellus} 10 (2):
179--187.
%
% \item [Stommel]H., A.B. Arons, and A.J. Faller. 1958. Some examples of
%   stationary flow patterns in bounded basins. \textit{Tellus} 10 (2):
%   179--187.

\bibitem{Stommel:1960}
Stommel H., and A.B. Arons.  1960. On the abyssal circulation of the
world ocean---II. An idealized model of the circulation pattern and
amplitude in oceanic basins. \textit{Deep-Sea Research} 6: 217--233.
%
% \item [Stommel]H., and A.B. Arons. 1960. On the abyssal circulation of
%   the world ocean---II. An idealized model of the circulation pattern
%   and amplitude in oceanic basins. \textit{Deep-Sea Research} 6:
%   217--233.

\bibitem{Stommel:1989}
Stommel H.M., and D.W. Moore.  1989. \textit{An Introduction to the
  Coriolis Force}.  Cambridge: University Press.
%
% \item [Stommel]H.M., and D.W. Moore. 1989. \textit{An Introduction to
%   the Coriolis Force}.  Cambridge: University Press.

\bibitem{Stott:2000}
Stott P.A., S.F.B. Tett, G.S. Jones, M.R. Allen, J.F.B. Mitchell and
G.J. Jenkins 2000. External Control of 20th Century Temperature by
Natural and Anthropogenic Forcings. \textit{Science} 290 (5499):
2133-2137.
%
% \item [Stott]P.A., S.F.B. Tett, G.S. Jones, M.R. Allen,
%   J.F.B. Mitchell and G.J. Jenkins 2000. External Control of 20th
%   Century Temperature by Natural and Anthropogenic
%   Forcings. \textit{Science} 290 (5499): 2133-2137.

\bibitem{Strub:1997}
Strub P.T., T.K. Chereskin, P.P. Niiler, C. James, and M.D. Levine.
1997. Altimeter-derived variability of surface velocities in the
California Current System 1. Evaluation of \textsc{Topex} altimeter
velocity resolution.  \textit{Journal of Geophysical Research} 102
(C6): 12,727--12,748.
%
% \item [Strub]P.T., T.K. Chereskin, P.P. Niiler, C. James, and
%   M.D. Levine.  1997. Altimeter-derived variability of surface
%   velocities in the California Current System 1. Evaluation of
%   \textsc{Topex} altimeter velocity resolution.  \textit{Journal of
%     Geophysical Research} 102 (C6): 12,727--12,748.

\bibitem{SUN:1985}
Working Group on Symbols, Units and Nomenclature in Physical
Oceanography. 1985. \textit{The International System of units (SI) in
  oceanography}. \textsc{iapso} Paris: \textsc{Unesco} Technical
Papers in Marine Science 45: 124.
%
% \item [SUN]Working Group on Symbols, Units and Nomenclature in
%   Physical Oceanography. 1985. \textit{The International System of
%     units (SI) in oceanography}. \textsc{iapso} Paris: \textsc{Unesco}
%   Technical Papers in Marine Science 45: 124.

\bibitem{Sverdrup:1947}
Sverdrup H.U.  1947. Wind-driven currents in a baroclinic ocean: with
application to the equatorial currents of the eastern Pacific.
\textit{Proceedings of the National Academy of Sciences} 33 (11):
318--326.
%
% \item [Sverdrup]H.U. 1947. Wind-driven currents in a baroclinic ocean:
%   with application to the equatorial currents of the eastern Pacific.
%   \textit{Proceedings of the National Academy of Sciences} 33 (11):
%   318--326.

\bibitem{Sverdrup:1942}
Sverdrup H.U., M.W. Johnson, and R.H. Fleming. 1942. \textit{The
  Oceans: Their Physics, Chemistry, and General Biology}.  Englewood
Cliffs, New Jersey: Prentice-Hall.
%
% \item [Sverdrup]H.U., M.W. Johnson, and
%   R.H. Fleming. 1942. \textit{The Oceans: Their Physics, Chemistry,
%     and General Biology}.  Englewood Cliffs, New Jersey:
%   Prentice-Hall.

\bibitem{SWAMP:1985} 
SWAMP Group Sea Wave Modeling Project. 1985. \textit{Ocean Wave
  Modeling}. New York: Plenum Press.
%
% \item [SWAMP Group]Sea Wave Modeling Project. 1985. \textit{Ocean Wave
%   Modeling}. New York: Plenum Press.

\bibitem{Swenson:1990}
Swenson K.R., and A.E. Shaw.  1990. The Argos system: Monitoring the
world's environment. \textit{Oceanography} 3 (1): 60--61.
%
% \item [Swenson]K.R., and A.E. Shaw. 1990. The Argos system: Monitoring
%   the world's environment. \textit{Oceanography} 3 (1): 60--61.

\bibitem{Takayabu:1999}
Takayabu Y.N., T. Ihuchi, M. Kachi, A. Shibata, and
H. Kanzawa. 1999. Abrupt termination of the 1997--98 El Nino in
response to a Madden-Julian oscillation. \textit{Nature} 402 (6759):
279--282.
%
% \item [Takayabu]Y.N., T. Ihuchi, M. Kachi, A. Shibata, and
%   H. Kanzawa. 1999. Abrupt termination of the 1997--98 El Nino in
%   response to a Madden-Julian oscillation. \textit{Nature} 402 (6759):
%   279--282.

\bibitem{Tapley:2001}
Tapley B.D., and M.-C. Kim.  2001. Applications to geodesy. In
\textit{Satellite Altimetry and Earth Sciences}. Edited by L.-L. Fu
and A.  Cazenave. 371--406. San Diego: Academic Press.
%
% \item [Tapley]B.D., and M.-C. Kim. 2001. Applications to geodesy. In
%   \textit{Satellite Altimetry and Earth Sciences}. Edited by L.-L. Fu
%   and A.  Cazenave. 371--406. San Diego: Academic Press.

\bibitem{Taylor:1921}
Taylor G.I.  1921. Experiments with rotating
fluids. \textit{Proceedings Royal Society (London)} A 100: 114--121.
%
% \item [Taylor]G.I. 1921. Experiments with rotating
%   fluids. \textit{Proceedings Royal Society (London)} A 100: 114--121.

\bibitem{Taylor:2000}
Taylor P.K. Editor.  2000. Intercomparison and validation of
ocean-atmosphere energy flux fields: Final Report of the Joint World
Climate Research Program and Scientific Committee on Ocean Research
Working Group on Air-sea Fluxes, \textit{World Climate Research
  Program Report} \textsc{wcrp}-112: 303.
%
% \item [Taylor]P.K. Editor. 2000. Intercomparison and validation of
%   ocean-atmosphere energy flux fields: Final Report of the Joint World
%   Climate Research Program and Scientific Committee on Ocean Research
%   Working Group on Air-sea Fluxes, \textit{World Climate Research
%     Program Report} \textsc{wcrp}-112: 303.

\bibitem{Taylor:2001}
Taylor P. K., E.F. Bradley, C.W. Fairall, D. Legler, J. Schultz,
R.A. Weller and G.H. White. 2001. Surface fluxes and surface reference
sites. In: \textit{Observing the Oceans in the 21st Century}. Edited
by C.J. Koblinsky and N.R. Smith. Melbourne, Bureau of Meteorology:
177--197.
%
% \item [Taylor]P. K., E.F. Bradley, C.W. Fairall, D. Legler,
%   J. Schultz, R.A. Weller and G.H. White. 2001. Surface fluxes and
%   surface reference sites. In: \textit{Observing the Oceans in the
%     21st Century}. Edited by C.J. Koblinsky and N.R. Smith. Melbourne,
%   Bureau of Meteorology: 177--197.

\bibitem{Tchernia:1980}
Tchernia P.  1980. \textit{Descriptive Regional Oceanography}. Oxford:
Pergamon Press.
%
% \item [Tchernia]P. 1980. \textit{Descriptive Regional
%   Oceanography}. Oxford: Pergamon Press.

\bibitem{Tennekes:1990}
Tennekes H., and J.L. Lumley.  1990. \textit{A First Course in
  Turbulence}.  Boston: MIT Press.
%
% \item [Tennekes]H., and J.L. Lumley. 1990. \textit{A First Course in
%   Turbulence}.  Boston: MIT Press.

\bibitem{Thurman:1985}
Thurman H.V.  1985. \textit{Introductory Oceanography}. Fourth
ed. Columbus: Charles E. Merrill Publishing Company.
%
% \item [Thurman]H.V. 1985. \textit{Introductory Oceanography}. Fourth
%   ed. Columbus: Charles E. Merrill Publishing Company.

\bibitem{Titov:1997}
Titov V.V. and F.I. Gonzalez.  1997. Implementation and testing of the
Method of Splitting Tsunami (\textsc{most}) model. \textsc{Noaa}
Pacific Marine Environmental Laboratory Contribution 1927: 14.
%
% \item [Titov]V.V. and F.I. Gonzalez. 1997. Implementation and testing
%   of the Method of Splitting Tsunami (\textsc{most})
%   model. \textsc{Noaa} Pacific Marine Environmental Laboratory
%   Contribution 1927: 14.

\bibitem{Toggweiler:1994}
Toggweiler J.R.  1994. The ocean's overturning
circulation. \textit{Physics Today} 47 (11): 45--50.
%
% \item [Toggweiler]J.R. 1994. The ocean's overturning
%   circulation. \textit{Physics Today} 47 (11): 45--50.

\bibitem{Toggweiler:2008}
Toggweiler J. R. and J. Russell 2008. Ocean circulation in a warming
climate. \textit{Nature} 451 (7176): 286--288.
%
% \item [Toggweiler]J. R. and J. Russell 2008. Ocean circulation in a
%   warming climate. \textit{Nature} 451 (7176): 286--288.

\bibitem{Tolmazin:1985}
Tolmazin D.  1985. \textit{Elements of Dynamic Oceanography}. Boston:
Allen and Unwin.
%
% \item [Tolmazin]D. 1985. \textit{Elements of Dynamic
%   Oceanography}. Boston: Allen and Unwin.

\bibitem{Tomczak:1994}
Tomczak M., and J.S. Godfrey.  1994. \textit{Regional Oceanography: An
  Introduction}. London: Pergamon.
%
% \item [Tomczak]M., and J.S. Godfrey. 1994. \textit{Regional
%   Oceanography: An Introduction}. London: Pergamon.

\bibitem{Tomczak:1999}
Tomczak M.  1999. Some historical, theoretical and applied aspects of
quantitative water mass analysis. \textit{Journal of Marine Research}
57 (2): 275--303.
%
% \item [Tomczak]M. 1999. Some historical, theoretical and applied
%   aspects of quantitative water mass analysis. \textit{Journal of
%     Marine Research} 57 (2): 275--303.

\bibitem{Trenberth:1987}
Trenberth K.E., and D.J. Shea.  1987. On the evolution of the Southern
Oscillation. \textit{Monthly Weather Review} 115: 3078--3096.
%
% \item [Trenberth]K.E., and D.J. Shea. 1987. On the evolution of the
%   Southern Oscillation. \textit{Monthly Weather Review} 115:
%   3078--3096.

\bibitem{Trenberth:1989}
Trenberth K.E., W.G. Large, and J.G. Olson.  1989. The effective drag
coefficient for evaluating wind stress over the
oceans. \textit{Journal of Climate}, 2: 1507--1516.
%
% \item [Trenberth]K.E., W.G. Large, and J.G. Olson. 1989. The effective
%   drag coefficient for evaluating wind stress over the
%   oceans. \textit{Journal of Climate}, 2: 1507--1516.

\bibitem{Trenberth:1990}
Trenberth K.E., W.G. Large, and J.G. Olson.  1990. The mean annual
cycle in global ocean wind stress. \textit{Journal of Physical
  Oceanography} 20 (11): 1742--1760.
%
% \item [Trenberth]K.E., W.G. Large, and J.G. Olson. 1990. The mean
%   annual cycle in global ocean wind stress. \textit{Journal of
%     Physical Oceanography} 20 (11): 1742--1760.

\bibitem{Trenberth:1994}
Trenberth K.E., and A. Solomon.  1994. The global heat balance: heat
transports in the atmosphere and ocean. \textit{Climate Dynamics} 10
(3): 107--134.
%
% \item [Trenberth]K.E., and A. Solomon. 1994. The global heat balance:
%   heat transports in the atmosphere and ocean. \textit{Climate
%     Dynamics} 10 (3): 107--134.

\bibitem{Trenberth:1997a}
Trenberth K.E.  1997. The use and abuse of climate
models. \textit{Nature} 386 (6621): 131--133.
%
% \item [Trenberth]K.E. 1997. The use and abuse of climate
%   models. \textit{Nature} 386 (6621): 131--133.

\bibitem{Trenberth:1997b}
Trenberth K.E.  1997. The definition of El Ni\~{n}no. \textit{Bulletin
  of the American Meteorological Society} 78 (12): 2771--2777.
%
% \item [Trenberth]K.E. 1997. The definition of El
%   Ni\~{n}no. \textit{Bulletin of the American Meteorological Society}
%   78 (12): 2771--2777.

\bibitem{Trenberth:2001}
Trenberth K.E. and J.M. Caron.  2001. Estimates of meridional
atmospheric and oceanic heat transports. \textit{Journal of Climate}
14 (16): 3433--3443.
%
% \item [Trenberth]K.E. and J.M. Caron. 2001. Estimates of meridional
%   atmospheric and oceanic heat transports. \textit{Journal of Climate}
%   14 (16): 3433--3443.

\bibitem{Uchida:1998}
Uchida H., S. Imawaki, and J.-H. Hu.  1998. Comparisons of Kuroshio
surface velocities derived from satellite altimeter and drifting buoy
data. \textit{Journal of Oceanography} 54: 115--122.
%
% \item [Uchida]H., S. Imawaki, and J.-H. Hu. 1998. Comparisons of
%   Kuroshio surface velocities derived from satellite altimeter and
%   drifting buoy data. \textit{Journal of Oceanography} 54: 115--122.

\bibitem{Uppala:2005}
Uppala S.M., and P.W. K\r{a}llberg, A.J. Simmons, U. Andrae, V. Da
Costa Bechtold, M. Fiorino, J. K. Gibson, J. Haseler, A. Hernandez,
G. A. Kelly, X. Li, K. Onogi, S. Saarinen, N. Sokka, R. P. Allan,
E. Andersson, K. Arpe, M. A. Balmaseda, A. C. M. Beljaars, L. Van De
Berg, J. Bidlot, N. Bormann, S. Caires, F. Chevallier, A. Dethof,
M. Dragosavac, M. Fisher, M. Fuentes, S. Hagemann, E. H\'{o}lm,
B. J. Hoskins, L. Isaksen, P.A.E.M. Janssen, R. Jenne, A. P. McNally,
J.-F. Mahfouf, J.-J. Morcrette, N. A. Rayner, R. W. Saunders,
P. Simon, A. Sterl, K. E. Trenberth, A. Untch, D. Vasiljevic,
P. Viterbo, J. Woollen. 2005. The \textsc{era}--40
re-analysis. \textit{Quarterly Journal of the Royal Meteorological
  Society} 131(612): 2961--3012.
%
% \item [Uppala]S.M., and P.W. K\r{a}llberg, A.J. Simmons, U. Andrae,
%   V. Da Costa Bechtold, M. Fiorino, J. K. Gibson, J. Haseler,
%   A. Hernandez, G. A. Kelly, X. Li, K. Onogi, S. Saarinen, N. Sokka,
%   R. P. Allan, E. Andersson, K. Arpe, M. A. Balmaseda,
%   A. C. M. Beljaars, L. Van De Berg, J. Bidlot, N. Bormann, S. Caires,
%   F. Chevallier, A. Dethof, M. Dragosavac, M. Fisher, M. Fuentes,
%   S. Hagemann, E. H\'{o}lm, B. J. Hoskins, L. Isaksen,
%   P.A.E.M. Janssen, R. Jenne, A. P. McNally, J.-F. Mahfouf,
%   J.-J. Morcrette, N. A. Rayner, R. W. Saunders, P. Simon, A. Sterl,
%   K. E. Trenberth, A. Untch, D. Vasiljevic, P. Viterbo,
%   J. Woollen. 2005. The \textsc{era}--40
%   re-analysis. \textit{Quarterly Journal of the Royal Meteorological
%     Society} 131(612): 2961--3012.

\bibitem{Ursell:1950}
Ursell F.  1950. On the theoretical form of ocean swell on a rotating
earth. \textit{Monthly Notices Royal Astronomical Society, Geophysical
  Supplement} 6 (1): G1--G8.
%
% \item [Ursell]F. 1950. On the theoretical form of ocean swell on a
%   rotating earth. \textit{Monthly Notices Royal Astronomical Society,
%     Geophysical Supplement} 6 (1): G1--G8.

\bibitem{vanMeurs:1998}
van Meurs P. 1998. Interactions between near-inertial mixed layer
currents and the meso\-scale: The importance of spatial variability in
the vorticity field. \textit{Journal of Physical Oceanography} 28 (7):
1363--1388.
%
% \item [van Meurs]P. 1998. Interactions between near-inertial mixed
%   layer currents and the meso\-scale: The importance of spatial
%   variability in the vorticity field. \textit{Journal of Physical
%     Oceanography} 28 (7): 1363--1388.

\bibitem{Vesecky:1982}
Vesecky J.F., and R.H. Stewart.  1982. The observation of ocean
surface phenomena using imagery from the Seasat synthetic aperture
radar: An assessment.  \textit{Journal of Geophysical Research} 87
(C5): 3397--3430.
%
% \item [Vesecky]J.F., and R.H. Stewart. 1982. The observation of ocean
%   surface phenomena using imagery from the Seasat synthetic aperture
%   radar: An assessment.  \textit{Journal of Geophysical Research} 87
%   (C5): 3397--3430.

\bibitem{vonArx:1962} 
von Arx~W.S. 1962. \textit{An Introduction to Physical
  Oceanography}. Reading, Massachusetts: Addison-Wesley.
%
% \item [von Arx]W.S. 1962. \textit{An Introduction to Physical
%   Oceanography}. Reading, Massachusetts: Addison-Wesley.

\bibitem{WAMDI:1988} 
WAMDI Group (S. Hasselmann, K. Hasselmann, E. Bauer,
P.A.E.M. Jans\-sen, G.J. Komen, L. Bertotti, P. Lionello,
A. Guillaume, V.C. Cardone, J.A. Greenwood, M. Reistad, L. Zambresky,
and J.A. Ewing). 1988. The WAM model---A third generation wave
prediction model. \textit{Journal of Physical Oceanography} 18:
1775--1810.
%
% \item [WAMDI Group]S. Hasselmann, K. Hasselmann, E. Bauer,
%   P.A.E.M. Jans\-sen, G.J. Komen, L. Bertotti, P. Lionello,
%   A. Guillaume, V.C. Cardone, J.A. Greenwood, M. Reistad,
%   L. Zambresky, and J.A. Ewing. 1988. The WAM model---A third
%   generation wave prediction model. \textit{Journal of Physical
%     Oceanography} 18: 1775--1810.

\bibitem{Warren:1973}
Warren B.A.  1973. Transpacific hydrographic sections at Latitudes
$\degrees{43}$~S and~$\degrees{28}$~S: The \textsc{scorpio}
Expedition--II. Deep Water. \textit{Deep-Sea Research} 20: 9--38.
%
% \item [Warren]B.A. 1973. Transpacific hydrographic sections at
%   Latitudes 43\degrees\ S and 28\degrees\ S: The \textsc{scorpio}
%   Expedition--II. Deep Water. \textit{Deep-Sea Research} 20: 9--38.

\bibitem{WCRP:1995}
WCRP World Climate Research Program.  1995. \textit{Proceedings of the
  Workshop on Global Coupled General Circulation Models}. World
Meteorological Organization/World Climate Research Program, WCRP-87
(WMO/TD Number 655).
%
% \item [WCRP]World Climate Research Program. 1995. \textit{Proceedings
%   of the Workshop on Global Coupled General Circulation Models}. World
%   Meteorological Organization/World Climate Research Program, WCRP-87
%   (WMO/TD Number 655).

\bibitem{Weaver:2004}
Weaver A.J. and C. Hillaire-Marcel 2004. Global Warming and the Next
Ice Age. \textit{Science} 304 (5669): 400--402.
%
% \item [Weaver]A.J. and C. Hillaire-Marcel 2004. Global Warming and the
%   Next Ice Age. \textit{Science} 304 (5669): 400--402.

\bibitem{Webb:2001}
Webb D.J., and N. Suginohara.  2001. Vertical mixing in the ocean.
\textit{Nature} 409 (6816): 37.
%
% \item [Webb]D.J., and N. Suginohara. 2001. Vertical mixing in the
%   ocean.  \textit{Nature} 409 (6816): 37.

\bibitem{Webster:1968}
Webster F.  1968. Observations of inertial-period motions in the deep
sea. Reviews of Geophysics 6 (4): 473--490.
%
% \item [Webster]F. 1968. Observations of inertial-period motions in the
%   deep sea. Reviews of Geophysics 6 (4): 473--490.

\bibitem{Webster:1992}
Webster P.J., and R. Lukas.  1992. \textsc{toga coare}: The Coupled
Ocean-Atmosphere Response Experiment. \textit{Bulletin American
  Meteorological Society} 73 (9): 1377--1416.
%
% \item [Webster]P.J., and R. Lukas. 1992. \textsc{toga coare}: The
%   Coupled Ocean-Atmosphere Response Experiment. \textit{Bulletin
%     American Meteorological Society} 73 (9): 1377--1416.

\bibitem{Weller:1985}
Weller R.A., J.P. Dean, J. Marra, J.F. Price, E.A. Francis, and D.C.
Boardman. 1985. Three--dimensional flow in the upper
ocean. \textit{Science} 227: 1552--1556.
%
% \item [Weller]R.A., J.P. Dean, J. Marra, J.F. Price, E.A. Francis, and
%   D.C.  Boardman. 1985. Three--dimensional flow in the upper
%   ocean. \textit{Science} 227: 1552--1556.

\bibitem{Weller:1996}
Weller R.A., and A.J. Plueddmann.  1996. Observations of the
  vertical structure of the oceanic boundary layer. \textit{Journal of
    Geophysical Research} 101 (C4): 8,789--8,806.
%
% \item [Weller]R.A., and A.J. Plueddmann. 1996. Observations of the
%   vertical structure of the oceanic boundary layer. \textit{Journal of
%     Geophysical Research} 101 (C4): 8,789--8,806.

\bibitem{Wentz:1984}
Wentz P.J., S. Peteherych, and L.A. Thomas.  1984. A model function
for ocean radar cross sections at 14.6 GHz. \textit{Journal of
  Geophysical Research} 89 (C3): 3689--3704.
%
% \item [Wentz]P.J., S. Peteherych, and L.A. Thomas. 1984. A model
%   function for ocean radar cross sections at 14.6 GHz. \textit{Journal
%     of Geophysical Research} 89 (C3): 3689--3704.

\bibitem{West:1982}
West G.B.  1982. Mean Earth ellipsoid determined from Seasat 1
altimetric observations. \textit{Journal of Geophysical Research} 87
(B7): 5538--5540.
%
% \item [West]G.B. 1982. Mean Earth ellipsoid determined from Seasat 1
%   altimetric observations. \textit{Journal of Geophysical Research} 87
%   (B7): 5538--5540.

\bibitem{White:1996}
White G. Editor.  1996. \textsc{wcrp} Workshop on Air-Sea Flux Fields
for Forcing Ocean Models and Validating GCMs. Geneva: World
Meteorological Organization Report WCRP--95 (WMO/TD Number 762).
%
% \item [White]G. Editor. 1996. \textsc{wcrp} Workshop on Air-Sea Flux
%   Fields for Forcing Ocean Models and Validating GCMs. Geneva: World
%   Meteorological Organization Report WCRP--95 (WMO/TD Number 762).

\bibitem{White:1998}
White W.B., and D.R. Cayan.  1998. Quasi-periodicity and global
symmetries in interdecadal upper ocean temperature
variability. \textit{Journal of Geophysical Research} 103 (C10):
21,335--21,354.
%
% \item [White]W.B., and D.R. Cayan. 1998. Quasi-periodicity and global
%   symmetries in interdecadal upper ocean temperature
%   variability. \textit{Journal of Geophysical Research} 103 (C10):
%   21,335--21,354.

\bibitem{Whitham:1974}
Whitham G.B.  1974. \textit{Linear and Nonlinear Waves}.  New York:
John Wiley.
%
% \item [Whitham]G.B. 1974. \textit{Linear and Nonlinear Waves}.  New
%   York: John Wiley.

\bibitem{Whittaker:1963}
Whittaker E.T., and G.N. Watson.  1963. \textit{A Course of Modern
  Analysis}. 4th ed.  Cambridge: University Press.
%
% \item [Whittaker]E.T., and G.N. Watson. 1963. \textit{A Course of
%   Modern Analysis}. 4th ed.  Cambridge: University Press.

\bibitem{Whitworth:1985}
Whitworth T., and R.G. Peterson.  1985. Volume transport of the
  Antarctic Circumpolar Current from bottom pressure
  measurements. \textit{Journal of Physical Oceanography} 15 (6):
  810--816.
%
% \item [Whitworth]T., and R.G. Peterson. 1985. Volume transport of the
%   Antarctic Circumpolar Current from bottom pressure
%   measurements. \textit{Journal of Physical Oceanography} 15 (6):
%   810--816.

\bibitem{Wiegel:1964}
Wiegel R.L.  1964. \textit{Oceanographical Engineering}.  Englewood
Cliffs, New Jersey: Prentice Hall.
%
% \item [Wiegel]R.L. 1964. \textit{Oceanographical Engineering}.
%   Englewood Cliffs, New Jersey: Prentice Hall.

\bibitem{Wilson:1960}
Wilson W.D.  1960. Equation for the speed of sound in sea
water. \textit{Journal of the Acoustical Society of America} 32 (10):
1357.
%
% \item [Wilson]W.D. 1960. Equation for the speed of sound in sea
%   water. \textit{Journal of the Acoustical Society of America} 32
%   (10): 1357.

\bibitem{Woodruff:1987}
Woodruff S.D., R.J. Slutz, R.L. Jenne, and P.M. Steurer. 1987. A
comprehensive ocean--atmosphere data set. \textit{Bulletin American
  Meteorological Society} 68: 1239--1250.
%
% \item [Woodruff]S.D., R.J. Slutz, R.L. Jenne, and
%   P.M. Steurer. 1987. A comprehensive ocean--atmosphere data
%   set. \textit{Bulletin American Meteorological Society} 68:
%   1239--1250.

\bibitem{Wooster:1960}
Wooster W.S.  1960. Investigations of equatorial
undercurrents. \textit{Deep-Sea Research} 6 (4): 263--264.
%
% \item [Wooster]W.S. 1960. Investigations of equatorial
%   undercurrents. \textit{Deep-Sea Research} 6 (4): 263--264.

\bibitem{Wooster:1969}
Wooster W.S., A.J. Lee, and G. Dietrich.  1969. Redefinition of
salinity.  \textit{Deep-Sea Research} 16 (3): 321--322.
%
% \item [Wooster]W.S., A.J. Lee, and G. Dietrich. 1969. Redefinition of
%   salinity.  \textit{Deep-Sea Research} 16 (3): 321--322.

\bibitem{Worthington:1981}
Worthington L.V.  1981. The water masses of the World Ocean: Some
results of a fine-scale census. In: \textit{Evolution of Physical
  Oceanography: Scientific surveys in honor of Henry Stommel}. Edited
by B. A. Warren and C. Wunsch. 42--69. Cambridge: Massachusetts
Institute of Technology.
%
% \item [Worthington]L.V. 1981. The water masses of the World Ocean:
%   Some results of a fine-scale census. In: \textit{Evolution of
%     Physical Oceanography: Scientific surveys in honor of Henry
%     Stommel}. Edited by B. A. Warren and C. Wunsch. 42--69. Cambridge:
%   Massachusetts Institute of Technology.

\bibitem{Wunsch:1996}
Wunsch C.  1996. \textit{The Ocean Circulation Inverse Problem}.
  Cambridge: University Press.
%
% \item [Wunsch]C. 1996. \textit{The Ocean Circulation Inverse Problem}.
%   Cambridge: University Press.

\bibitem{Wunsch:2002a}
Wunsch C.  2002. Ocean observations and the climate forecast
  problem.In: \textit{Meteorology at the Millennium}, Edited by
  R.P. Pearce. London: Royal Meteorological Society: 233--245.
%
% \item [Wunsch]C. 2002. Ocean observations and the climate forecast
%   problem.In: \textit{Meteorology at the Millennium}, Edited by
%   R.P. Pearce. London: Royal Meteorological Society: 233--245.

\bibitem{Wunsch:2002b}
Wunsch C.  2002. What is the thermohaline circulation?
  \textit{Science} 298 (5596): 1179--1180.
%
% \item [Wunsch]C. 2002b. What is the thermohaline circulation?
%   \textit{Science} 298 (5596): 1179--1180.

\bibitem{Wust:1964}
Wust G.  1964. The major deep--sea expeditions and research
  vessels 1873--1960. \textit{Progress in Oceanography} 2: 3--52.
%
% \item [Wust]G. 1964. The major deep--sea expeditions and research
%   vessels 1873--1960. \textit{Progress in Oceanography} 2: 3--52.

\bibitem{Wyrtki:1975}
Wyrtki K.  1975. El Ni\~{n}o---The dynamic response of the equatorial
Pacific Ocean to atmospheric forcing. \textit{Journal of Physical
  Oceanography} 5 (4): 572--584.
%
% \item [Wyrtki]K. 1975. El Ni\~{n}o---The dynamic response of the
%   equatorial Pacific Ocean to atmospheric forcing. \textit{Journal of
%     Physical Oceanography} 5 (4): 572--584.

\bibitem{Wyrtki:1979}
Wyrtki K.  1979. Sea level variations: monitoring the breath of the
Pacific. \textit{EOS Transactions of the American Geophysical Union}
60 (3): 25-27.
%
% \item [Wyrtki]K. 1979. Sea level variations: monitoring the breath of
%   the Pacific. \textit{EOS Transactions of the American Geophysical
%     Union} 60 (3): 25-27.

\bibitem{Wyrtki:1985}
Wyrtki K.  1985. Water displacements in the Pacific and the genesis of
El Ni\~{n}o cycles. \textit{Journal of Geophysical Research} 90 (C4):
7129-7132.
%
% \item [Wyrtki]K. 1985. Water displacements in the Pacific and the
%   genesis of El Ni\~{n}o cycles. \textit{Journal of Geophysical
%     Research} 90 (C4): 7129-7132.

\bibitem{Xie:1997}
Xie P., and P.A. Arkin.  1997. Global precipitation: A 17-year monthly
analysis based on gauge observations, satellite estimate, and
numerical model outputs. \textit{ Bulletin of the American
  Meteorological Society} 78 (1): 2539--2558.
%
% \item [Xie]P., and P.A. Arkin. 1997. Global precipitation: A 17-year
%   monthly analysis based on gauge observations, satellite estimate,
%   and numerical model outputs. \textit{ Bulletin of the American
%     Meteorological Society} 78 (1): 2539--2558.

\bibitem{Yelland:1996}
Yelland M., and P.K. Taylor.  1996. Wind stress measurements from the
open ocean. \textit{Journal of Physical Oceanography} 26 (4):
541--558.
%
% \item [Yelland]M., and P.K. Taylor. 1996. Wind stress measurements
%   from the open ocean. \textit{Journal of Physical Oceanography} 26
%   (4): 541--558.

\bibitem{Yelland:1998}
Yelland M.J., B.I. Moat, P.K. Taylor, R.W. Pascal, J. Hutchings and
V.C. Cornell. 1998. Wind stress measurements from the open ocean
corrected for airflow distortion by the ship. \textit{Journal of
  Physical Oceanography} 28 (7): 1511--1526.
%
% \item [Yelland]M.J., B.I. Moat, P.K. Taylor, R.W. Pascal, J. Hutchings
%   and V.C. Cornell. 1998. Wind stress measurements from the open ocean
%   corrected for airflow distortion by the ship. \textit{Journal of
%     Physical Oceanography} 28 (7): 1511--1526.

\bibitem{Yu:1999}
Yu X., and M.J. McPhaden.  1999. Dynamical analysis of seasonal and
interannual variability in the equatorial Pacific. \textit{Journal of
  Physical Oceanography} 29 (9): 2350--2369.
%
% \item [Yu]X., and M.J. McPhaden. 1999. Dynamical analysis of seasonal
%   and interannual variability in the equatorial
%   Pacific. \textit{Journal of Physical Oceanography} 29 (9):
%   2350--2369.

\bibitem{Zahn:1994}
Zahn R.  1994. Core correlations. \textit{Nature} 371 (6495):
289--290.
%
% \item [Zahn]R. 1994. Core correlations. \textit{Nature} 371 (6495):
%   289--290.
\end{thebibliography}

% \end{description}
